\section{Introduction and main result}
\label{sec:introduction}

Let $H$ be the regular hexagon of side length one.  The problem is to decide
whether seven open equilateral triangles of the same side length can cover
$H$.  The use of open triangles is essential at boundary handoffs: when two
open traces meet at a common endpoint, that endpoint is still uncovered.

\begin{theorem}[Main theorem]
\label{thm:main}
The regular side-one hexagon $H$ cannot be covered by seven open unit
equilateral triangles.
\end{theorem}

The compactness and scaling lemma proved in
Proposition~\ref{prop:open-closed-scaled} gives the following equivalent
form.

\begin{corollary}[Expanded closed formulation]
\label{cor:expanded-closed}
For every $L>1$, the regular hexagon $H_L$ of side length $L$ cannot be
covered by seven closed unit equilateral triangles.
\end{corollary}

The proof is organized by mechanism rather than by the eventual case tree.
Section~\ref{sec:structural-reductions} fixes the geometric model, assigns the seven
roles, and proves exhaustive center- and vertex-role classifications.  It
also transfers the supercritical-row count from actual maximal boundary
reaches to strictly selected handoff demands.

Section~\ref{sec:length} establishes direct one-dimensional trace bounds on
the boundary, the six radial arms, the three main diagonals, and the full
skeleton when the additional hypotheses needed for a skeleton estimate are
present.  These estimates dispose of the coarse branches and several
exceptional positive-support configurations.

Section~\ref{sec:exact-demand} develops exact local admissibility and capped
demand maps.  Exact center-trace and radial-exit formulas turn a center gap or
a missing midpoint into boundary and radial demands.  Iteration of the local
maps returns a demand that is incompatible with the remaining trace capacity.
This section contains the delicate $\CEone/\CEtwo$ branches.

Section~\ref{sec:area} normalizes the area of a unit equilateral triangle to
one.  It proves unconditional local square-loss estimates and a separate
loss estimate for the recurrent \straddlinghangul{} (straddling)
$\Tlike$ configuration.
Their cyclic sum closes the remaining $\CEzero$ branches with one or at
least two supercritical rows.

Section~\ref{sec:ab-core} treats the all-$\Vdzero$, exactly-one-supercritical,
zero-gap configuration without any center-class assumption.  Six common
radial points and three asymmetric points are excluded directly from the six
actual vertex roles; only the unique supercritical row uses an exact
corner-clipped $AB$-frontier.  Convexity forces the resulting nine-point
witness into the center role, while a caliper inequality rules out its
enclosure by an open unit equilateral triangle.

Finally, Section~\ref{sec:assembly} gives the exhaustive routing table and
proves Theorem~\ref{thm:main}.  Long formulas are collected in
Appendix~\ref{app:formulas}.  Appendix~\ref{app:certificates} records the
finite caliper certificate, and Appendix~\ref{sec:exact-mixed-overlap} gives
the exact rational and global-Bernstein certificate for the two mixed
overlaps.  No interval subdivision, branch-and-bound, plot, floating-point
optimization, or unproved structural conjecture is used as a logical
dependency.
