\section{Strategy 2: exact boundary--radial demand propagation}
\label{sec:exact-demand}

This section treats the configurations in which a coarse length sum does not
by itself record enough information.  The mechanism is always the same.  A
center trace fixes boundary inputs and complementary radial demands; an exact
local map propagates these data through nonsupercritical rows; and the
returning demand exceeds the remaining boundary or radial capacity.

Actual maximal reaches continue to be denoted by $(A_i,B_i,C_i)$, while
lowercase letters denote prescribed demands.  The only machine-assisted
statement used in this section is the rational interval certificate
Theorem~\ref{thm:cert-407} in Appendix~\ref{app:certificates}.  All other
estimates in this section are proved analytically.  In particular, no
empirical branch catalogue and no formal root from a discarded algebraic
component is used.

\subsection{The exact local feasible set}

Put
\[
 u=\left(\frac12,\frac{\sqrt3}{2}\right),\qquad
 v=\left(\frac12,-\frac{\sqrt3}{2}\right).
\]
For $0\le a,b,c\le1$ define
\[
 K(a,b,c)=\conv\{0,au,bv,c(u+v)\}.
\]
Thus $a,b$ are lower demands on the two incident boundary rays and $c$ is a
lower demand on the inward radial ray.

\begin{definition}
\label{def:admissible-demands}
The local admissible set is
\[
 \begin{aligned}
 \mathcal A=\{(a,b,c)\in[0,1]^3:\;&K(a,b,c)\text{ is contained}\\
 &\text{in a closed unit equilateral triangle}\}.
 \end{aligned}
\]
For $a,c\in[0,1]$ put
\[
 \begin{aligned}
 B_c(a)&=\max\{b:(a,b,c)\in\mathcal A\},\\
 F_c(a)&=\min\{B_c(a),1-a\},\\
 G_c(a)&=1-F_c(a).
 \end{aligned}
\]
\end{definition}

The distinction between demands and actual reaches is important.  If a role
has actual reaches $(A,B,C)$ and $A\ge a$, $C\ge c$, then $(a,B,c)$ is a
demand triple realized by the same role.  If in addition $A+B\le1$, then
\begin{equation}
 B\le F_c(a).
 \label{eq:safe-capped-bound}
\end{equation}
No assertion about the type of a maximizing triangle is required.

\begin{proposition}[Exact admissible set and radial envelope]
\label{prop:exact-admissible-set}
\label{prop:local-admissible}
Put
\[
 s=a+b,\qquad d=a^2+ab+b^2,\qquad
 m=\min\{a,b\},\qquad M=\max\{a,b\},
\]
and
\[
 q=s^4-s^2+ab.
\]
Define
\begin{align*}
 F_L(a,b,c)&=c^4-c^2+mc-m^2,\\
 F_T(a,b,c)&=(s^2-1)c^2+Mc-M^2,\\
 F_S(a,b,c)&=(m^2-1)c^2+(2mM^2+M)c+M^4-M^2.
\end{align*}
Then $\mathcal A=\mathcal A_L\cup\mathcal A_T\cup\mathcal A_S$, where
\begin{align*}
 \mathcal A_L&=\{d\le1, s\le1, q\le0, F_L\le0\},\\
 \mathcal A_T&=\{d\le1, s\le1, q\ge0, F_T\le0, c\le2M\},\\
 \mathcal A_S&=\{d\le1, s>1, F_S\le0, c\le\tfrac12\}.
\end{align*}
All variables in these three sets are also constrained to $[0,1]$.

For $d\le1$, the maximal radial demand is
\begin{equation}
 c_{\max}(a,b)=
 \begin{cases}
  1,&a=b=0,\\
  C_L(m),&s\le1, q\le0, (a,b)\ne(0,0),\\
  C_T(m,M),&s\le1, q>0,\\
  C_S(m,M),&s>1,
 \end{cases}
 \label{eq:radial-envelope}
\end{equation}
where $C_L(m)$ is the unique root in $[\sqrt3/2,1]$ of
\[
 z^4-z^2+mz-m^2=0,
\]
and
\[
 C_T(m,M)=\frac{2M}{1+\sqrt{4s^2-3}},
\qquad
 C_S(m,M)=
 \frac{M(2mM+1)-M\sqrt{4d-3}}{2(1-m^2)}.
\]
If $d>1$, the radial envelope is undefined.  At $q=0$ the two subcritical
formulas agree and equal $s$.
\end{proposition}

\begin{proof}
If $s>0$ and $cs\le ab$, then $c/a+c/b\le1$ (with the zero-coordinate
cases obtained by continuity), so $c(u+v)$ lies in
$\conv\{0,au,bv\}$.  Its minimum enclosing equilateral side is the diameter
\[
 \sqrt{a^2+ab+b^2}.
\]
Assume now that $cs>ab$.  The four points occur cyclically as
$0,bv,c(u+v),au$.  For three outward unit normals separated by
$120^\circ$, the required side equals $2/\sqrt3$ times the sum of the three
support values.  On an angular cell with fixed support points this sum has
second derivative equal to its negative.  Hence an angular minimum occurs
when a normal is perpendicular to one of the four hull edges.  The four
resulting side lengths are
\begin{align*}
 L_{0A}&=b+\max\{a,c\},&
 L_{B0}&=a+\max\{b,c\},\\
 L_{AC}&=
 \begin{cases}
 (a^2+bc)/\sqrt{a^2-ac+c^2},&a\ge c,\\
 c(a+b)/\sqrt{a^2-ac+c^2},&a<c\le a+b,\\
 c^2/\sqrt{a^2-ac+c^2},&c>a+b,
 \end{cases}
\end{align*}
and $L_{CB}$ is obtained by interchanging $a,b$.  Thus the minimum side is
the minimum of these four expressions.

Ordering $a,b$ as $m\le M$, squaring the positive support equations gives
$F_L=0,F_T=0,F_S=0$ in the three respective contact regimes; the inactive
support inequalities give $q\le0,q\ge0,s>1$.  Squaring creates one spurious
component in each of the last two cells.  In the $T$ cell the two roots are
\[
 \frac{2M}{1+\sqrt{4s^2-3}},
 \qquad
 \frac{2M}{1-\sqrt{4s^2-3}},
\]
and $c\le2M$ selects the first.  In the $S$ cell the smaller root lies below
$1/2$ and the other above $1/2$; hence $c\le1/2$ is exactly the geometric
selector.  The $L$ fiber is the interval from zero to its unique selected
root.  Solving the selected equations gives \eqref{eq:radial-envelope}.
This also proves that $\mathcal A$ is coordinatewise down-closed.
\end{proof}

\subsection{The exactly-one-supercritical all-$\Vdzero$ branch}

For a center interval, call the nonempty closed set missed by its two open
endpoint roles a \emph{V-gap}.  It may be a singleton.  If the maximal
closed center trace is $[s,t]$, open coverage gives the weak bounds
$b_i\ge s$ and $a_{i+1}\ge1-t$; thus none of the arguments below discards a
singleton gap.

\begin{proposition}[CE1 one-gap five-map obstruction]
\label{prop:ce1-one-gap}
Assume that every vertex role is $\Vdzero$, $N_+=1$, and the center role is
CE1.  If its boundary trace contains a V-gap, the roles do not cover $H$.
\end{proposition}

\begin{proof}
By midpoint locality, rows $1,\ldots,5$ contain their own radial midpoints;
hence they are nonsupercritical and row $0$ is the unique supercritical
row.  Put
\[
 R=\lambda,\quad w=1-R,\quad E=\sqrt{1-Rw},\quad
 \eta=1-E,\quad P=\eta E,
\]
and let $A=C_0$, $D=C_2$ in Proposition~\ref{prop:center-exact-formulas}.
Then, with $X=R-D$, $m=A/R$ and
$H=(\eta+A+D)/(2R)=s/2$, the exact strict domain is
\begin{equation}
\begin{gathered}
 A>0,\quad D>0,\quad A+wD<P,\quad D+RA\ge P,\\
 A<\frac w2,\quad D<\frac R2,\quad RD-wA>0,
\end{gathered}
\label{eq:ce1-normal-domain}
\end{equation}
and the six complementary demands are
\[
 c_0=\eta+A+D,\quad c_1=1-\frac DR,\quad c_2=1-D,
 \quad c_3=1-m,\quad c_4=1-A,\quad c_5=1-\frac Aw.
\]
The gap gives $B_0\ge s$ and $A_1\ge X$.  Boundary propagation through the
five nonsupercritical rows therefore gives
\[
 A_0\ge Z:=
 (G_{c_5}\circ G_{c_4}\circ G_{c_3}\circ G_{c_2}\circ G_{c_1})(X),
 \qquad A_0\le B_{c_0}(s).
\]
It remains to prove the reverse strict inequality.

Repeated use of \eqref{eq:S2-capped-duality} reduces it to
\begin{equation}
 (G_{c_2}\circ G_{c_3}\circ G_{c_4})(H)>1-X.
 \label{eq:ce1-suffix}
\end{equation}
The elementary low-root estimates give
\[
 e(A)<X,\qquad H>A.
\]
At row $4$, every label except $T_+^{\rm hi}$ already yields
$G_{1-A}(H)>1-X$.  On $T_+^{\rm hi}$ its selector forces $X>1/2$.
Indeed, if $X\le1/2$, the selector and the two center inequalities give
\[
 Q(A):=\eta+P+wA-2R(2A+5A^2)\le0,
 \qquad 0<A<A_0:=P-w(R-\tfrac12).
\]
The quadratic $Q$ is strictly concave and $Q(0)=\eta+P=Rw>0$.
Rationalize by
\[
 k=\frac{R}{1+E},\qquad
 R=\frac{k(2-k)}{1-k^2},\quad
 E=\frac{1-k+k^2}{1-k^2},\quad
 \eta=\frac{k(1-2k)}{1-k^2}.
\]
When $R\le1/2$, one has $k\le2-\sqrt3<27/100$ and $A_0\ge P$, while
\[
 Q(P)=\frac{k(1-2k)(-f_8(k))}{(1-k^2)^5},
\]
where
\[
 f_8(k)=16k^8-77k^7+175k^6-244k^5+199k^4
       -101k^3+13k^2+12k-3.
\]
For $0\le k\le27/100$, put
\[
 q(k)=\frac{2333}{5}k^3-303k^2+26k+12.
\]
Then
\[
 f_8'(k)-q(k)
 =\frac{k^3}{5}\left(640k^4+k^2(5250-2695k)+1647-6100k\right)
 \ge0.
\]
Writing $t=27/100-k$, one also has
\[
 q(k)\ge
 \frac{30576939}{5000000}+\frac{1089743}{50000}t>0,
\]
because the difference between the two sides is
\[
 -\frac{t(100t-27)(116650t+12759)}{25000}\ge0.
\]
Thus $f_8$ is increasing.  At $k_0=2-\sqrt3$,
\[
 f_8(k_0)=77724-44874\sqrt3<0,
 \qquad 3\cdot44874^2-77724^2=7452>0.
\]
Hence $f_8(k)<0$ for $k\le k_0$, and so $Q(P)>0$.
When $R>1/2$, $0<A_0<P$ and
\[
 Q(A_0)=\frac{(1-2k)(-g_5(k))}{2(1-k^2)^3},\qquad
 g_5(k)=32k^5-118k^4+150k^3-86k^2+18k-1.
\]
At $k_0=2-\sqrt3$,
$g_5(k_0)=3471-2004\sqrt3<0$ because
$3\cdot2004^2-3471^2=207$.  If $y=4k-1\in[0,1]$, then
\[
 8g_5'(k)=5y^4-39y^3+78y^2-51y-29
 \le y(-34y^2+78y-51)-29<0,
\]
because the displayed quadratic has discriminant $-852$.  Thus $g_5$
decreases and remains negative for $k>k_0>1/4$, so
$Q(A_0)>0$.  In either range concavity makes $Q(A)>0$ throughout the
allowed interval, contradicting $Q(A)\le0$ and proving $X>1/2$.

Put $p_1=G_{1-A}(H)$.  If row $3$ is not $T_+^{\rm hi}$, then
$p_1\le A+e(A)<3A+5A^2<29/64<1/2$, and
$2R(H-m)=\eta+D-A>\eta-P>0$.  Thus both Full branches are impossible;
on $L$, $T_-$, or the low-$c$ tie one has $F_{1-m}(p_1)\le p_1$, proving
\eqref{eq:ce1-suffix}.  We use the following elementary property of a
selected $T_+$ arc.  Put $d=1-c$, let $q=G_c(p)$, and write $u=q-p$.
The selected equation is
\[
 f(q):=(1-q)(q-d)=g(u):=(1-d)^2u(2-u).
\]
On the interior of the arc, $f',g'>0$.  If
\[
 A_0=f'(q)=1+d-2q,\qquad
 B_0=g'(u)=2(1-d)^2(1-u),
\]
then
\[
 u'=\frac{A_0}{B_0},\qquad
 u''=\frac{2((1-d)^2A_0^2-B_0^2)}{B_0^3}.
\]
Moreover
\[
 B_0-(1-d)A_0=(1-d)(1-3d+2p+2du)>0
\]
and
\[
 B_0-A_0\ge(1-d)(1-2d)>0.
\]
Thus $p=q-u$ is increasing and strictly convex as a function of $q$.
Consequently $q=G_{1-d}(p)$ is increasing and strictly concave on each
selected arc; a tie endpoint follows by continuity.

When $d<1-\sqrt3/2$, the arc endpoints are
$(d,d)$ and $(e(d),d+e(d))$.  Its chord and
$e(d)<2d/(1-2d)$ give
\[
 q\ge p+\frac{d}{e(d)-d}(p-d)
 >p+\frac{1-2d}{1+2d}(p-d).
\]
This is stronger than both the row-$4$ coefficient $1-4d$ and the row-$3$
coefficient $1-5d$.  In the low-$c$ row-$3$ range
$1-\sqrt3/2\le d<1/5$, the other endpoint is
$(h(1-d),1-h(1-d))$, and the chord coefficient is
\[
 \frac{1-2h(1-d)}{h(1-d)-d}>\frac13>1-5d.
\]
Indeed $h(1-d)<(3+d)/7$: substitution of $(3+d)/7$ into its defining
upward quadratic gives
\[
 \frac{-1+30d-65d^2+16d^3+4d^4}{49}>0.
\]
Here $d\ge1-\sqrt3/2>2/15$, and
$-1+30d-65d^2$ is increasing and already equals $83/45$ at $2/15$.
For $d\ge1/5$, extensivity alone is stronger than the row-$3$ estimate.

Applying these chord bounds first with $d=A$ and then with $d=m$ proves,
without an omitted selected branch,
\begin{align*}
 p_1&>L_1:=(2-4A)H-(1-4A)A,\\
 p_2:=G_{1-m}(p_1)&>L_2:=(2-5m)L_1-(1-5m)m.
\end{align*}

Finally let
\[
 D_0=P-RA,\qquad
 D_h=A(4R-1)+10RA^2-\eta,\qquad x=Rw.
\]
Feasibility puts $D_0\le D\le D_h$.  We first prove that the actual
feasible value satisfies $D<1/10$.  Since
\[
 P=\frac{xE}{1+E}<\frac x2,\qquad
 \eta=\frac{x}{1+E}>\frac x2,
\]
the contrary assumption $D\ge1/10$ and $A+wD<P$ give
\[
 A<\overline A:=\frac{w(5R-1)}{10}.
\]
The function $D_h(A)$ is increasing, so
\[
 D\le D_h(A)<D_h(\overline A)
 <U(R):=\overline A(4R-1)+10R\overline A^2-\frac x2.
\]
Direct expansion yields
\[
 \frac1{10}-U(R)=-\frac{R}{10}P_4(R),
 \qquad
 P_4(R)=25R^4-60R^3+26R^2+22R-14.
\]
For $y=2R-1\in[0,1]$,
\[
 16P_4(R)=25y^4-20y^3-106y^2+124y-39
 \le-101y^2+124y-39<0.
\]
The last quadratic has discriminant $-380$.  Hence $U(R)<1/10$, a
contradiction, and therefore $D<1/10$.

It remains to compare $L_2$ with $2D+3D^2$.  Put
\[
 J(D)=L_2(D)-\frac{23}{10}D.
\]
Since
\[
 L_2-2D-3D^2-J(D)=3D\left(\frac1{10}-D\right)>0,
\]
it is enough to prove $J(D)>0$.  Exact differentiation gives
\[
 J'(D)=\frac{S(R,A)}{10R^2},\qquad
 S(R,A)=100A^2-(40R+50)A+R(20-23R).
\]
The inequality $D_0\le D_h$ is equivalent to
\[
 x\le A(5R-1+10RA).
\]
Because $A<P<x/2\le1/8$,
\[
 A>L:=\frac{4x}{25R-4}.
\]
Also $\partial_A S=200A-40R-50<-45$, and direct substitution gives
\[
 S(R,L)=-\frac{R q_3(R)}{(25R-4)^2},
\]
where
\[
 q_3(R)=8775R^3-14260R^2+7928R-1120.
\]
For $y=2R-1$,
\[
 8q_3(R)=8775y^3-2195y^2+997y+3007\ge812>0.
\]
Thus $J'(D)<0$ and $J(D)\ge J(D_h)$.

At $D=D_h$ one has $H=2A+5A^2$.  Write $L_{2,h}=L_2(D_h)$.
Expansion gives
\[
 L_{2,h}-A(1+4R)=\frac{A}{R^2}\mathcal Q(R,A),
\]
where
\[
\begin{aligned}
 \mathcal Q(R,A)={}&100A^3R-40A^2R^2-30A^2R
 +12AR^2-15AR+5A\\
 &-4R^3+5R^2-R.
\end{aligned}
\]
On $0\le A\le x/2$,
\[
 \partial_A^2\mathcal Q=20R(30A-4R-3)<0.
\]
Its two endpoint values are
\[
 \mathcal Q(R,0)=x(4R-1)>0,\qquad
 \mathcal Q\left(R,\frac x2\right)=\frac{x}{2}p(R),
\]
where
\[
 p(R)=25R^5-30R^4+20R^3-3R^2-7R+3.
\]
For $y=2R-1$,
\[
 32p(R)=25y^5+65y^4+90y^3+106y^2-35y+5>0,
\]
because the terms of degree at least three are nonnegative and
$106y^2-35y+5$ has discriminant $-895$.  Concavity therefore gives
$L_{2,h}>A(1+4R)$.

On the other hand, $A<P=\eta E$ and $A<P<x/2$ imply
\[
 \frac{D_h}{A}
 =4R-1+10RA-\frac{\eta}{A}
 <C_0:=4R-2+5Rx-\frac x2.
\]
Here we used
\[
 \frac1E>1+\frac x2,
 \qquad
 (1-x)\left(1+\frac x2\right)^2
 =1-\frac{x^2(3+x)}4<1.
\]
Finally,
\[
 1+4R-\frac{23}{10}C_0=\frac{h_3(R)}{20},
 \qquad
 h_3(R)=230R^3-253R^2-81R+112.
\]
Since $h_3''(R)=46(30R-11)\ge184$, strong convexity at $R_0=20/23$
gives
\[
 h_3(R)\ge
 \frac{788}{529}-\frac{(17/23)^2}{368}
 =\frac{289695}{194672}>0.
\]
Consequently
\[
 J(D_h)>A\left(1+4R-\frac{23}{10}C_0\right)>0,
\]
and hence
\[
 p_2>L_2>2D+3D^2.
\]

The low root $e(D)$ is the smaller root of
\[
 H_D(z)=z^2-(1-D)z+(1-D)^2-(1-D)^4,
\]
and direct substitution gives
$H_D(2D+3D^2)=D^2(8D^2+19D-2)<0$.  Hence
$e(D)<2D+3D^2<p_2$.  Every row-$2$ label now yields
$G_{1-D}(p_2)>1-X$, proving \eqref{eq:ce1-suffix}.

The first and fifth maps are extensive, and therefore
\[
 Z>1-H=1-\frac s2.
\]
The diameter endpoint
$\beta(s)=(-s+\sqrt{4-3s^2})/2$ satisfies
$B_{c_0}(s)\le\beta(s)<1-s/2$.  Thus $Z>B_{c_0}(s)$, contradicting the two
bounds on $a_0$.
\end{proof}

\begin{proposition}[CE2 one-gap five-map obstruction]
\label{prop:ce2-one-gap}
Assume that every vertex role is $\Vdzero$, $N_+=1$, and the center role is
CE2.  If exactly one of its two boundary traces contains a V-gap, the roles
do not cover $H$.
\end{proposition}

\begin{proof}
Again row $0$ is uniquely supercritical.  Put
\[
 R=\frac{x}{x+y},\quad w=1-R,\quad E=\sqrt{1-Rw},\quad
 \eta=1-E,\quad P=\eta E,
\]
and
\[
 \alpha=u-R,\qquad \delta=v-w,\qquad k=\eta+\alpha+\delta.
\]
The exact CE2 domain becomes
\begin{equation}
 \alpha,\delta>0,\qquad
 \delta+R\alpha<P,\qquad \alpha+w\delta<P,
 \label{eq:ce2-normal-domain}
\end{equation}
with $x=k/w$, $y=k/R$, and demands
\[
 \begin{aligned}
 c_0&=k, & c_1&=1-\delta/R,\\
 c_2&=1-\delta, & c_3&=1-\min\{\delta/w,\alpha/R\},\\
 c_4&=1-\alpha, & c_5&=1-\alpha/w.
 \end{aligned}
\]
Write $G_i=G_{c_i}$ for $1\le i\le5$.
Suppose the gap is in $[y,v]$.  Its endpoint bounds give the initial input
$z_0=1-v=R-\delta$ and target $y$.  From
\eqref{eq:ce2-normal-domain}, the concavity of
\[
 \pi(q)=(\eta+q)(1-2q)-2qw,\qquad
 \pi(0)=\eta,\quad \pi(P)=\eta(\eta+2ER^2),
\]
and \eqref{eq:low-root-bounds},
\begin{equation}
 z_0>\frac{\eta+\alpha}{w}>
 \frac{2\alpha}{1-2\alpha}>e(\alpha).
 \label{eq:ce2-initial-threshold}
\end{equation}
Put $Q=y/2=k/(2R)$.  We also have
\begin{equation}
 \min\{e(\alpha),e(\delta)\}<Q.
 \label{eq:ce2-two-threshold}
\end{equation}
For if both roots were at least $Q$, then
$\alpha,\delta>Q/(2(1+Q))$; eliminating $\eta$ with the first inequality in
\eqref{eq:ce2-normal-domain} would give $H(Q)>0$, where
\[
 H(q)=\left(2R-\frac1{1+q}\right)(E+R)-2R^2-
 \frac{w}{2(1+q)}.
\]
But $H'(q)>0$, $Q<w/(2R)$, and
\[
 H\left(\frac w{2R}\right)=\frac{R(2RE-R-1)}{R+1}<0,
\]
the last sign following from
$(R+1)^2-4R^2E^2=(1-R)(4R^3+3R+1)>0$.

If $e(\alpha)<Q$, row $4$ and
\eqref{eq:high-demand-threshold} give $z_4>1-Q$; otherwise
\eqref{eq:ce2-two-threshold} gives $e(\delta)<Q$, and
\eqref{eq:ce2-initial-threshold} makes row $2$ give $z_2>1-Q$.  Extensivity
of the remaining maps yields
\[
 Z_R=(G_5\circ G_4\circ G_3\circ G_2\circ G_1)(1-v)>1-y/2.
\]
Moreover the two inequalities in \eqref{eq:ce2-normal-domain} imply
$E(\alpha+\delta)<\eta$, hence $x^2+xy+y^2<1$.  The exact inner selector at
the diameter endpoint is therefore active and
\[
 B_{c_0}(y)=\beta(y)<1-y/2.
\]
Thus $Z_R>B_{c_0}(y)$, contrary to the supercritical row's admissibility.
Reflection exchanges $(x,u,R,\alpha)$ with $(y,v,w,\delta)$ and reverses the
five maps, proving the other orientation.
\end{proof}

\begin{proposition}[Positive-gap all-$\Vdzero$, $N_+=1$]
\label{prop:nplus-one-all-vd0}
If the center role is CE1 or CE2, every vertex role is $\Vdzero$, and
$N_+=1$, then no cover of $H$ can have a boundary gap in the actual open
vertex-role traces.
\end{proposition}

\begin{proof}
The midpoint argument used above makes $T_0$ uniquely supercritical.  In an
assumed cover, every boundary gap in the vertex-role traces must lie in a
center trace.  CE1 therefore has the one-gap state excluded by
Proposition~\ref{prop:ce1-one-gap}.  For CE2, the exactly-one-gap state is
Proposition~\ref{prop:ce2-one-gap}; if both center intervals contain gaps, the
endpoint bounds and exact exits are those of
Lemma~\ref{lem:two-endpoint-capped-loss}, so the two far outgoing reaches sum
to less than one.  Rows $2,3,4$ would then have to cover more than three
boundary units, contradicting their three nonsupercritical caps.  This
exhausts the one- and two-gap states, including singleton gaps.  The zero-gap
state is intentionally owned by the center-independent obstruction of
Strategy~4.
\end{proof}

\subsection{The exactly-one-$T3$ branch}

\begin{proposition}[Exactly one T3-like row]
\label{prop:nplus-one-one-t3}
Assume the center role is CE1 or CE2, $N_+=1$, exactly one vertex role is
T3-like, and no role is Vd1 or Vd2.  Then the roles do not cover $H$.
\end{proposition}

\begin{proof}
Normalize the center midpoint to $M_0$.  A T3-like row misses its own
midpoint, a supercritical row misses all its local midpoints, and a Vd0 row
cannot rescue a neighboring midpoint.  Consequently, after reflection,
\[
 T_0\text{ is T3-like},\qquad M_1\in T_0,
 \qquad T_1\text{ is uniquely supercritical},
\]
and $T_2,\ldots,T_5$ are nonsupercritical Vd0 rows.

In $V_0$ wedge coordinates put
\[
 1\le D\le\frac2{\sqrt3},\quad E=\sqrt{4-3D^2},\quad
 R=\frac{D+E}{2},
\]
and let $a$ be the $e_{5,0}$ reach of $T_0$.  Its interval on $r_1$ is
\[
 [c,u],\qquad c=\frac{D(1+a)-1}{R},\qquad
 u=1-\frac RD+a,
\]
where
$E/(2D)\le a\le(4-3D+E)/(4D)$.  Its own-radial exit is $x_0=aD/R$.
For $B(c)=\mathcal B(c)$ and $A(c)=1-B(c)$, direct substitution gives
\[
 c-\frac{x_0(2-x_0)}{1+x_0}
 =\frac{2N(D,a)}{(D+E)(2Da+D+E)},
\]
where
\[
 N=4D^2a^2+D^2a+D^2-DEa+DE-2Da-D-E.
\]
This convex quadratic is nonnegative: on $1\le D\le8/7$ its minimum on
the allowed interval is at $a=E/(2D)$, and squaring reduces the sign to
$4(D-1)(7D^3-10D^2-8D+12)\ge0$; on
$8/7\le D\le2/\sqrt3$ its critical value is positive because
$(9D-10)E+9D^2-6D-4>0$.  Before using monotonicity, note explicitly that
\[
 x_0=\frac{aD}{R}\le\frac{4-3D+E}{4R}\le\frac12;
\]
the second inequality is equivalent, using $2R=D+E$, to $D\ge1$.
Also $c\le1/2$ because $M_1\in[c,u]$, and hence
$0\le A(c)=1-\mathcal B(c)\le1/2$.  Since
$X(2-X)/(1+X)$ is increasing on $[0,1/2]$, this proves
\begin{equation}
 x_0\le A(c).
 \label{eq:t3-radial-edge}
\end{equation}

Radial coverage forces the supercritical row's own demand $c_1\ge c$.
Lemma~\ref{lem:free-supercritical-envelope} gives
$b_1<B(c_1)\le B(c)$.  On $e_{5,0}$ the far row $T_5$ is forced to reach
at least $h\ge B(c)$.  Indeed this is $h\ge1-a$ unless a CE2 interval hides
the boundary gap.  In the hiding case the side model gives
$T\le x_0$, and \eqref{eq:t3-radial-edge} again gives
$h\ge1-T\ge B(c)$.  Therefore
\[
 \sum_{i=2}^5(a_i+b_i)
 \ge (1-b_1)+1+1+1+h>4,
\]
contrary to the four row caps.  The case $c=1/2$ is already impossible
because the strict supercritical feasible set is empty there.
\end{proof}

\subsection{The nonsupercritical CE1/CE2 boundary packages}

\begin{proposition}[All-Vd0 boundary loss]
\label{prop:nplus-zero-all-vd0}
Assume that $T_C$ is CE1 or CE2, every vertex role is Vd0, and
\[
 A_i+B_i\le1\qquad(0\le i\le5).
\]
Then the seven roles do not cover $H$.
\end{proposition}

\begin{proof}
If the center boundary traces are already covered by the open vertex roles,
then those six roles cover all of $\partial H$.  Put
$W_i=U_i\cap\partial H$.  These are relatively open subsets of the
connected circle $\partial H$, each of length at most one.  At least two are
nonempty, and a finite relatively open cover of a connected space cannot
have its nonempty members pairwise disjoint.  Thus two overlap on a
positive-length relatively open set, whence
\[
 6=\Haus(\partial H)<\sum_{i=0}^5\Haus(W_i)
 \le\sum_{i=0}^5(A_i+B_i)\le6,
\]
a contradiction.

Suppose next that $T_C$ is CE1 and its trace $[s,t]\subset e_{0,1}$
contains a boundary gap.  Put $u=1-t$ and $w=t-s$.  Boundary coverage gives
$B_0\ge s$ and $A_1\ge u$.  Since the center has no trace on $e_{5,0}$,
\[
 A_0+B_5\ge1,\qquad A_0+B_0\le1,
\]
and hence $B_5\ge B_0\ge s$.  The exact CE1 formulas, after putting
$R=\lambda$ in the orientation selected there, have the form
\[
 c_1=u/R,\qquad
 c_5=1-\left(u-\frac{R}{1+\sqrt{1-R+R^2}}
                   -\frac{R}{1-R}w\right).
\]
All hypotheses of Lemma~\ref{lem:one-side-capped-loss} hold.  Therefore the
outgoing reaches of rows $1$ and $5$ satisfy
$\widehat b_1+\widehat b_5<1$, where
\[
 \widehat b_1\le F_{c_1}(u),\qquad
 \widehat b_5\le F_{c_5}(s).
\]
Rows $2,3,4$ must then supply boundary length at least
\[
 (1-\widehat b_1)+1+1+(1-\widehat b_5)>3,
\]
contrary to their three row caps.

Now let $T_C$ be CE2.  If exactly one of $[x,u]$, $[y,v]$ contains a gap,
reflect so that it is $[y,v]$.  The interval $[x,u]$ is covered by its
endpoint roles, so the same endpoint propagation gives inputs $y$ and
$1-v$.  With
\[
 R=\frac{x}{x+y},\qquad s=y,\qquad u'=1-v,\qquad w'=v-y,
\]
the CE2 coupling and exit formulas are exactly those of
Lemma~\ref{lem:one-side-capped-loss}.  The preceding three-row contradiction
applies unchanged.  If both center intervals contain gaps, put
\[
 p=1-u,\quad q=1-v,\quad r=\frac{x}{x+y},\quad
 w=\frac{y}{x+y}.
\]
The far endpoint roles have inputs at least $p,q$ and radial demands
$p/w,q/r$.  Lemma~\ref{lem:two-endpoint-capped-loss} again makes their two
outgoing reaches sum to less than one, and the same middle three-row budget
is impossible.  These are the no-, one-, and two-active-interval states,
and are exhaustive.
\end{proof}

We next treat the additional T3-like rows in the $N_+=0$ branch.  The
following local facts also reappear later.

\begin{lemma}[T3-like midpoint and side tradeoff]
\label{lem:t3-midpoint-tradeoff}
Let $T_i$ be T3-like.  Then $M_i\notin T_i$.  After applying the closed-trace
domination of Proposition~\ref{prop:t3-translation}, suppose the selected
adjacent support is on $r_{i+1}$ and $M_{i+1}$ belongs to the dominated
trace.  If $b$ is its boundary reach toward $V_{i+1}$, $c$ its exit on its
own arm, and $\ell$ its entry on $r_{i+1}$, all measured from the relevant
vertex, then
\begin{equation}
 b+c<1,\qquad b+\ell>1.
 \label{eq:t3-side-tradeoff}
\end{equation}
Consequently two adjacent T3-like traces that cover each other's midpoint,
whose selected supports point toward one another, cannot cover both outer
half-arms if no other role has positive support there.
\end{lemma}

\begin{proof}
Normalize at $V_0$ with wedge coordinates $(x,y)$ and metric
$x^2+y^2-xy$.  Suppose first, toward the own-midpoint claim, that a unit
triangle with two outside vertices $A,B$ contains both $(0,0)$ and
$(1/2,1/2)$.  Diameter one implies that an outside vertex has a negative
coordinate and that each of its coordinates is strictly below one.  Order
$A,B$ and write
\[
 B-A=(r,s),\qquad C-A=(s,s-r),\qquad r^2+s^2-rs=1.
\]
Since $(0,0)$ lies in the triangle, for some $\lambda,\mu\ge0$ with
$\lambda+\mu\le1$,
\[
 A=-\lambda(r,s)-\mu(s,s-r).
\]
The midpoint condition is exactly
\[
 \lambda+\frac r2\ge0,\qquad
 \mu+\frac{s-r}{2}\ge0,\qquad
 \lambda+\mu+\frac s2\le1.
\]
Put $t=s-r$.  The four choices of negative coordinates of $A,B$ give the
required bounds on the third vertex as follows.
\begin{enumerate}
\item If $A_x,B_x<0$, then $C_x=A_x+s<1$ when $s\le1$.  When $s>1$,
the unit equation gives $r,t>0$, and $B_x<0$ gives $C_x<t<1$.
For the other coordinate, $C_y=B_y-r<1$ when $r\ge0$; when $r<0$, put
$q=-r+s$ to obtain
\[
 C_y\le q-\frac{q^2-1}{2}\le1.
\]
\item If $A_y,B_y<0$, the reflected argument gives the same two bounds.
\item If $A_x<0$ and $B_y<0$, the alternative $s>1$ would imply
$\mu>1-\lambda$, which is impossible.  Hence $C_x<1$.  Also,
$r<-1$ would imply $s<0$ and then $A_x\ge0$; consequently
$C_y=B_y-r\le1$.
\item If $A_y<0$ and $B_x<0$, reflection of the preceding case applies.
\end{enumerate}
In the $r<0$ entry, $q=-r+s$ and
$(-r)^2+s^2-rs=1$ give $(-r)s=q^2-1$, while
$\lambda\ge-r/2$ gives the displayed bound.  Thus every vertex satisfies
$x\le1,y\le1$, and only $C$ can meet either equality line.  Convexity makes
both adjacent-arm intersections zero-length, contradicting the T3-like
condition.  Hence $M_0\notin T_0$.

For the tradeoff, the translated T3-like trace has the exhaustive Type-II
form
\[
 \begin{aligned}
 (1-t)x+ty&\ge0,\\
 \beta+tx-y&\ge0,\\
 \beta+x-(1-t)y&\le z,
 \end{aligned}
 \qquad 0<t<1,\quad z=\sqrt{1-t+t^2},\quad0<\beta<z.
\]
For the selected support on $r_1$, substitution in the Type-II half-planes
gives
\[
 b=z-\beta,\qquad c=\frac{\beta}{1-t},\qquad
 \ell=\frac{\beta+1-z}{1-t}.
\]
The condition $M_1\in T$ is
$\beta\le z-(1+t)/2$.  Therefore
\[
 b+c\le z+\frac{t}{1-t}
 \left(z-\frac{1+t}{2}\right)
 =1-\frac{(1-z)^2}{2(1-t)}<1,
\]
whereas
\[
 b+\ell-1=\frac{t(1-z+\beta)}{1-t}>0.
\]
For a crossed adjacent pair, coverage forces
$c_i\ge\ell_{i+1}$ and $c_{i+1}\ge\ell_i$.  Combining these two
inequalities with \eqref{eq:t3-side-tradeoff} gives both
$b_i<b_{i+1}$ and $b_{i+1}<b_i$, a contradiction.
\end{proof}

\begin{lemma}[The support-isolated four-label inequality]
\label{lem:407-four-label-loss}
Assume $T_C$ is CE1 or CE2, $N_+=0$, no role is Vd1 or Vd2, and, after
normalization and reflection, $T_0$ is T3-like with selected adjacent
support on $r_1$.  Then the two endpoint rows in the isolated configuration
satisfy
\begin{equation}
 F_{c_5^\ast}(a_5^\ast)+F_{c_1^\ast}(a_1^\ast)<1,
 \label{eq:407-loss}
\end{equation}
where $a_1^\ast,a_5^\ast$ are the exact boundary inputs and
$c_1^\ast,c_5^\ast$ the exact radial demands defined below.
\end{lemma}

\begin{proof}
Use the CE1 side variables $0<\lambda<1$,
$\rho=\sqrt{1-\lambda+\lambda^2}$ and center slacks
\[
 X=F_0(O),\qquad Y=F_2(O).
\]
Then
\[
 a_C=\lambda-Y,\qquad
 \lambda s=X+Y+1-\rho,
\]
and
\[
 \gamma_1=\min\left\{\frac Y\lambda,
                 \frac{\rho-X-Y}{1-\lambda}\right\},\qquad
 \gamma_5=\min\left\{\frac X{1-\lambda},
                 \frac{\rho-X-Y}{\lambda}\right\}.
\]
For CE2 the second boundary interval is $[S,T]$, where
\[
 S=\frac{X+Y+1-\rho}{1-\lambda},\qquad T=X+\lambda.
\]

The T3-like normal form supplies $D>1$, $0<R<1$, and $\alpha,p\ge0$ with
\[
 R^2-DR+D^2=1,\qquad \alpha+p=1/D,\qquad
 q=1-p=\alpha+(D-1)/D<1/2.
\]
Its interval on $r_1$, measured from $V_1$, is
\[
 [c,u],\qquad c=Dq/R,\qquad u=q+(1-R)/D.
\]
For an initial trace $[0,p]$ and a center interval $J=[L,U]$, define
\[
 \Theta(p,J)=
 \begin{cases}
 1-p,&J=\varnothing\text{ or }p<L,\\
 1-\max\{p,U\},&p\ge L.
 \end{cases}
\]
Then
\[
 a_1^\ast=\Theta(p,[s,t]),\qquad
 a_5^\ast=\Theta(\alpha,[S,T]),
\]
with the second interval empty in CE1, and
\[
 c_5^\ast=1-\gamma_5,\qquad
 c_1^\ast=
 \begin{cases}
 c,&1-u\le\gamma_1\le1-c,\\
 1-\gamma_1,&\text{otherwise}.
 \end{cases}
\]

If $a_1^\ast+a_5^\ast>1$, the two caps already imply
$F_{c_5^\ast}(a_5^\ast)+F_{c_1^\ast}(a_1^\ast)<1$.  Assume the hard region
$a_1^\ast+a_5^\ast\le1$.  The following table is an exhaustive audit of the four
possible first labels; the middle column records the exact decisive
inequality.
\[
\begin{array}{c|c|c}
\text{first label}&\text{right labels}&\text{conclusion}\\ \hline
L&\mathrm{Full}&e(\gamma_5)<a_1^\ast\\
L&L,T_-&F_{c_5^\ast}(a_5^\ast)+F_{c_1^\ast}(a_1^\ast)<1\\
L&T_+^{\mathrm{hi}}&e(\gamma_5)<a_1^\ast\\
T_-&L,T_-&F_{c_5^\ast}(a_5^\ast)+F_{c_1^\ast}(a_1^\ast)<1\\
T_-&\mathrm{Full},T_+^{\mathrm{hi}}&F_{c_5^\ast}(a_5^\ast)<a_1^\ast\\
\mathrm{Full}&\text{all}&\text{impossible}\\
T_+^{\mathrm{hi}}&\mathrm{Full},T_+^{\mathrm{hi}}&\text{impossible}\\
T_+^{\mathrm{hi}}&L,T_-&F_{c_5^\ast}(a_5^\ast)+F_{c_1^\ast}(a_1^\ast)<1.
\end{array}
\]
We verify the nonformal entries.  Put
$\kappa=(1-\rho)/(1-\lambda)$.  From
$X+(1-\lambda)Y<\rho(1-\rho)$ one obtains
\begin{align}
 \gamma_1\ge a_C&\Longrightarrow e(\gamma_5)<a_C,
 \label{eq:407-core-estimate}\\
 S\le Y/\lambda&\Longrightarrow e(\gamma_5)<S.
 \label{eq:407-S-estimate}
\end{align}
For \eqref{eq:407-core-estimate}, one has
$\gamma_5<a_C-\kappa$ and
$a_C-\kappa<1/8$; then \eqref{eq:low-root-bounds} applies, and the remaining
comparison is
\[
 (a_C-\kappa)+5(a_C-\kappa)^2\le\kappa.
\]
After squaring its positive sides, the difference is
$\lambda(23\lambda^3+58\lambda^2+7\lambda+72)>0$.
For \eqref{eq:407-S-estimate}, the premise forces
$0<\lambda<3/8$ and
\[
 \gamma_5\le\frac X{1-\lambda}<\frac18,\qquad
 S\ge\frac{X+1-\rho}{1-2\lambda}.
\]
The concave quadratic in $X$ obtained from
$2X/(1-\lambda)+5X^2/(1-\lambda)^2<S$ is positive at both endpoints;
clearing radicals gives respectively the positive squares recorded in
\eqref{eq:407-core-estimate} and
$\lambda^2(1-2\lambda)^2(1-\lambda)^2(-R_8)$, where every Bernstein
coefficient of $-R_8$ on $[0,3/8]$ is positive.

The $L$ separation follows from its exact polynomial: if its output is
$z=e(\eta)$ at input $1-\beta$, then
\[
 \beta\ge z+\eta.
 \label{eq:407-L-separation}
\]
Indeed the selector polynomial
$P(x,z)=x^4-4x^3+5x^2-(2+z)x+z-z^2$ is strictly decreasing on the low
range and vanishes at $x=\eta$.  Equations
\eqref{eq:407-core-estimate}--\eqref{eq:407-L-separation}, with the three
possibilities for $\Theta$, prove every first-$L$ entry.  For a first $T_-$
label the exact root test
\[
 T_-(a,c)<z\iff c^2(a+z)^2-(a^2-ac+c^2)>0
\]
is increasing in $z$.  Substitution of $a_1^\ast$, followed by the center
inequality, proves $F_{c_5^\ast}(a_5^\ast)<a_1^\ast$ except in the low--low entries, which
are immediate from $T_-(a,c)\le\min\{a,1-a\}$ and $L<1/2$.
First-coordinate Full would force either
$X\ge(1-\lambda)\alpha$ and $Y\ge\lambda-\alpha$, contradicting
$s\le p$, or, in the CE2 overlap case, $S\ge1/2$, contradicting
$S\le\alpha<1/2$.

For a first $T_+^{\mathrm{hi}}$ label put $r=1-\lambda$,
$y=Y/\lambda$ and choose $\beta$ so that
\[
 m=\sqrt{\beta^2-\beta+1},\quad
 1-\gamma_5=\frac m{r+\beta},\quad
 F_{c_5^\ast}(a_5^\ast)=\frac{\beta m}{r+\beta}.
\]
The exact selector is
\begin{equation}
 \beta\ge\max\left\{r,\frac12,\frac{1-r^2}{1+2r}\right\},\qquad
 r\ge(1-\beta)(r+\beta)^2.
 \label{eq:407-high-domain}
\end{equation}
The center inequalities give $y<1/10$ and, with
\[
 y_*=\frac r{1-r}
 \left(\frac m{r+\beta}-\frac12-\frac{1-r}{1+\sqrt{r^2-r+1}}\right),
\]
give $y<y_*$ and
\[
 3y_*\le1-\frac{\beta m}{r+\beta}.
\]
This proves the right-$L$ entry by $e(y)<3y$.  It excludes right Full and
right high by the exact high-input filter.  For right $T_-$ with input
$a_C$, direct substitution gives a sum below one.  For input $q$, put
$c=1-y$, $q=tc$, and let $\widehat b_1=F_{c_1^\ast}(q)$.  The selected $T_-$ equations
give
\[
 \widehat b_1\le\kappa:=\frac{\sqrt{13}-1}{6},\qquad
 q\le\tau<\frac{93}{200},
\]
where $\tau\in(0,1/2)$ is the unique root of
$\tau^4-3\tau^3+3\tau^2-3\tau+1=0$.  In this CE2 overlap subcase the
support ordering gives $q>S$.  The common left-high identities are
\[
 S=S_0+\frac{1-r}{r}y,\qquad
 S_0=1-\frac{m}{r+\beta}+\frac{1-r}{1+\sqrt{r^2-r+1}}.
\]
Since $y>0$, we have the complete chain
\[
 S_0<S<q\le\tau<\frac{93}{200}.
\]
Thus the $S_0$ hypothesis of Theorem~\ref{thm:cert-407} holds; together
with the exact selector domain \eqref{eq:407-high-domain}, it gives
\[
 F_{c_5^\ast}(a_5^\ast)<\frac{5657}{10000}
 <\frac{7-\sqrt{13}}6.
\]
Thus the final sum is also below one.  The table is exhaustive, proving
\eqref{eq:407-loss}.
\end{proof}

\begin{proposition}[The $N_+=0$ T3-like branch]
\label{prop:nplus-zero-t3}
Assume that $T_C$ is CE1 or CE2, $N_+=0$, no vertex role is Vd1 or Vd2,
and at least one vertex role is T3-like.  Then the seven roles do not cover
$H$.
\end{proposition}

\begin{proof}
Normalize the unique center midpoint to $M_0$ and simultaneously apply the
closed-trace domination of Proposition~\ref{prop:t3-translation} to every
T3-like role.  If $T_0$ were not T3-like, a maximal consecutive block of
T3-like indices among $1,\ldots,5$ would have to match its roles bijectively
to the same block of uncovered midpoints.  The matching uses only adjacent
indices, because a T3-like role misses its own midpoint and Vd0 roles cannot
cover adjacent midpoints.  Its first two roles therefore form a crossed pair
forbidden by Lemma~\ref{lem:t3-midpoint-tradeoff}.  Hence $T_0$ is T3-like;
reflect so that it supports $r_1$.

The diagonal trace bounds from Section~\ref{sec:strategy1-length} imply that
there are at most two T3-like roles: if there were $k\ge3$, the center,
T3-like, and nonsupercritical Vd0 diagonal caps would give
\[
 6<\frac32+\frac{k}{2}+(6-k)\le6.
\]
Midpoint locality then forces $T_2,T_4,T_5$ to be Vd0.  Consequently $r_1$
has positive support only from $T_C,T_0,T_1$, and $r_5$ only from $T_C,T_5$.

The actual outgoing reaches of $T_1,T_5$ are bounded by the two safe maps in
Lemma~\ref{lem:407-four-label-loss}; an extra adjacent-ray demand on a
possible T3-like $T_1$ only shrinks its feasible set.  Thus their sum is
less than one.  Rows $T_2,T_3,T_4$ must cover more than three units of the
four intervening boundary edges, while their three nonsupercritical caps
sum to at most three.  This contradiction proves the proposition.
\end{proof}

\subsection{The exact capped map}

For $1/2<c<1$ put
\[
 \ell(c)=\frac c2\left(1-\sqrt{4c^2-3}\right),\qquad
 r(c)=c-\ell(c)
\]
when $c\ge\sqrt3/2$, and
\[
 h(c)=\frac{2c}{1+\sqrt{16c^2-3}}.
\]
Also define
\begin{align*}
 T_-(a,c)&=\frac{\sqrt{a^2-ac+c^2}}c-a,\\
 T_+(a,c)&=
 \frac{2(1-a^2)c^2}
 {2ac^2+c+\sqrt{(2ac^2+c)^2-4(1-c^2)(1-a^2)c^2}}.
\end{align*}

\begin{proposition}[Four-label capped map]
\label{prop:capped-demand-map}
For $1/2<c\le\sqrt3/2$,
\begin{equation}
 F_c(a)=
 \begin{cases}
  1-a,&0\le a\le1-c,\\
  T_+(a,c),&1-c<a<h(c),\\
  h(c),&a=h(c),\\
  T_-(a,c),&h(c)<a<c,\\
  1-a,&c\le a\le1.
 \end{cases}
 \label{eq:S2-capped-map-low}
\end{equation}
For $\sqrt3/2<c<1$,
\begin{equation}
 F_c(a)=
 \begin{cases}
  1-a,&0\le a\le1-c,\\
  T_+(a,c),&1-c<a\le\ell(c),\\
  \ell(c),&\ell(c)<a<r(c),\\
  T_-(a,c),&r(c)\le a<c,\\
  1-a,&c\le a\le1.
 \end{cases}
 \label{eq:S2-capped-map-high}
\end{equation}
Thus there are exactly four labels
\[
 \mathrm{Full},\qquad L,\qquad T_-,\qquad T_+^{\mathrm{hi}}.
\]
At $a=\ell(c)$ in \eqref{eq:S2-capped-map-high},
$F_c(a)=r(c)$; immediately to its right the value is $\ell(c)$.  This
downward jump is genuine.  The formal other root of the $T_+$ quadratic is
not feasible because it violates $c\le2\max\{a,F_c(a)\}$.

The maps $F_c$ are nonincreasing, the maps $G_c=1-F_c$ are nondecreasing
and extensive, and
\begin{equation}
 G_c(a)\le z\quad\Longleftrightarrow\quad
 G_c(1-z)\le1-a.
 \label{eq:S2-capped-duality}
\end{equation}
\end{proposition}

\begin{proof}
The cap $a+b\le1$ eliminates the $S$ cell of
Proposition~\ref{prop:exact-admissible-set}.  On the cap $b=1-a$, the $T$
inequality reduces to $M(c-M)\le0$; hence the Full face is feasible exactly
for $a\le1-c$ or $a\ge c$.  Off that face a maximal point lies on $F_L=0$
or $F_T=0$.  The $L$ equation has roots $\ell(c),r(c)$ and the selector
$q\le0$ keeps only the smaller coordinate.  The ordered $T$ halves give
respectively the displayed lower quadratic root $T_+$ and the root $T_-$.
Their order boundary is $a=b=h(c)$, while their $q=0$ boundaries are
$(\ell(c),r(c))$ and $(r(c),\ell(c))$.  These observations give
\eqref{eq:S2-capped-map-low}--\eqref{eq:S2-capped-map-high}, including all equality
assignments.

Down-closedness gives monotonicity.  Finally,
\[
 G_c(a)\le z\iff F_c(a)\ge1-z
 \iff(a,1-z,c)\in\mathcal A,\quad a+1-z\le1.
\]
Reflection $a\leftrightarrow b$ gives \eqref{eq:S2-capped-duality}.
\end{proof}

For $0<X<1-\sqrt3/2$ write
\[
 e(X)=\ell(1-X).
\]
The root equation gives the estimates
\begin{equation}
 X<e(X)<\frac{2X}{1-2X},\qquad
 e(X)\le2X+5X^2\quad(0<X\le1/8),
 \label{eq:low-root-bounds}
\end{equation}
and
\begin{equation}
 a>e(X)\quad\Longrightarrow\quad
 G_{1-X}(a)\ge1-e(X).
 \label{eq:high-demand-threshold}
\end{equation}
Indeed, substitution into
$z^2-(1-X)z+(1-X)^2-(1-X)^4$ gives the two comparisons, and
\eqref{eq:high-demand-threshold} is read directly from
\eqref{eq:S2-capped-map-high}.  We shall also use
$e(X)<2X+3X^2$ for $0<X\le1/10$, obtained from
$X^2(8X^2+19X-2)<0$.

\begin{lemma}[Free strict-supercritical envelope]
\label{lem:free-supercritical-envelope}
For $0\le c<1/2$,
\[
 \sup\{b:\exists a, (a,b,c)\in\mathcal A, a+b>1\}
 =\mathcal B(c):=\frac{c+\sqrt{c^2-8c+4}}2.
\]
The supremum is not attained.  For $c\ge1/2$ the strict feasible set is
empty.  The function $\mathcal B$ is strictly decreasing on $[0,1/2]$.
\end{lemma}

\begin{proof}
Lemma~\ref{lem:self-midpoint} excludes $c\ge1/2$.  On the boundary
$a=1-b$, a support rotation has strict slack precisely when
\[
 c<\frac{1-b^2}{2-b}.
\]
The right side decreases from $1/2$ to zero.  Solving equality gives the
displayed larger root.  Equality has no strict support slack, which explains
nonattainment.  Differentiation gives
\[
 \mathcal B'(c)=\frac12\left(1+\frac{c-4}{\sqrt{c^2-8c+4}}\right)<0,
\]
since $(4-c)^2-(c^2-8c+4)=12$.
\end{proof}

\subsection{Exact center traces and complementary demands}

The normalization in Proposition~\ref{prop:unique-center-midpoint} lets us
assume that the unique center midpoint is $M_0$.

\begin{proposition}[Exact CE1 and CE2 formulas]
\label{prop:center-exact-formulas}
In the CE1 case there are $0<\lambda<1$, $0\le s<t\le1$, and
$\rho=\sqrt{1-\lambda+\lambda^2}$ for which
\[
 T_C\cap e_{0,1}=[s,t]
\]
and
\begin{align*}
 C_0&=\rho+\lambda s-t-\lambda,&
 C_1&=1-\lambda s,&
 C_2&=t+\lambda-1.
\end{align*}
The exact domain is
\begin{gather*}
 C_0>0,\quad C_2>0,\quad
 \lambda s\le\tfrac12,\quad t<1-\tfrac\lambda2,\\
 t>\rho+\lambda s-\frac{1+\lambda}{2},\qquad
 t\ge\rho-\frac{\lambda^2}{1-\lambda}s.
\end{gather*}
The center exits on the six arms are
\begin{align*}
 d_0&=C_1,& d_1&=C_2/\lambda,\\
 d_2&=C_2,& d_3&=\min\{C_0/\lambda,C_2/(1-\lambda)\},\\
 d_4&=C_0,& d_5&=C_0/(1-\lambda).
\end{align*}

In the CE2 case write
\[
 T_C\cap e_{5,0}=[x,u],\qquad
 T_C\cap e_{0,1}=[y,v],\qquad S=x+y,\quad
 D=\sqrt{x^2+xy+y^2}.
\]
Then
\begin{gather*}
 0<x<u<1,\qquad0<y<v<1,\\
 (u+v)S-xy=D,\qquad uS\ge x,\quad vS\ge y,\\
 uS<x+y/2,\qquad vS<y+x/2,
\end{gather*}
where the two weak center inequalities are strict for closures of original
open center roles.  The six exits are
\[
 \begin{aligned}
 d_0&=1-\frac{xy}{S},&
 d_1&=\frac{vS-y}{x},&
 d_2&=\frac{vS-y}{S},\\
 d_3&=\min\left\{\frac{vS-y}{y},\frac{uS-x}{x}\right\},&
 d_4&=\frac{uS-x}{S},&
 d_5&=\frac{uS-x}{y}.
 \end{aligned}
\]
In either case the complementary demand on row $i$ is $c_i=1-d_i$;
$c_0\le1/2$ and $c_i>1/2$ for $i\ne0$.
\end{proposition}

\begin{proof}
In the affine coordinates
$X=V_0+b(V_1-V_0)+a(V_5-V_0)$, the CE1 triangle is cut out by
\[
 \begin{aligned}
 F_1&=\lambda b+(1-\lambda)a-\lambda s,\\
 F_2&=-b+\lambda a+t,\\
 F_0&=(1-\lambda)b-a+\rho+\lambda s-t.
 \end{aligned}
\]
Substitution of $O,M_0,\ldots,M_5$ and of the six radial parametrizations
gives the displayed domain and exits.  The last domain inequality is exactly
the absence of a positive interval on $e_{5,0}$.

For CE2, the side through the initial endpoints has outward normal
$(\sqrt3S,y-x)/(2D)$.  Rotating it by $\pm120^\circ$, the three support
constants are
\[
 \frac{\sqrt3(S-xy)}{2D},\qquad
 \frac{\sqrt3(vS-y)}{2D},\qquad
 \frac{\sqrt3(uS-x)}{2D}.
\]
Their sum is $\sqrt3/2$ exactly when $(u+v)S-xy=D$.  Substitution of the
midpoints gives the four remaining inequalities, and substitution of the
radial rays gives the six exits.  The inequalities $d_0\ge1/2>d_i$
for $i\ne0$ are precisely the exact-midpoint conditions.
\end{proof}

\subsection{Two reusable capped-loss inequalities}

\begin{lemma}[One-side capped loss]
\label{lem:one-side-capped-loss}
Let $0<R<1$, $S=\sqrt{1-R+R^2}$, and let $s,u,w>0$ satisfy
$s+u+w=1$ and $0<u<R$.  Put
\[
 \delta=\frac{R}{1+S},\qquad
 \gamma=u-\delta-\frac{R}{1-R}w,
\]
and assume $\gamma>0$.  Set
\[
 c_1=u/R,\qquad c_5=1-\gamma.
\]
Then
\begin{equation}
 F_{c_5}(s)+F_{c_1}(u)<1.
 \label{eq:one-side-loss}
\end{equation}
\end{lemma}

\begin{proof}
Put $\eta=(1-R)\delta=1-S$ and
\[
 \widehat b_5=F_{c_5}(s),\qquad
 \widehat b_1=F_{c_1}(u).
\]
The center identity may be written
\begin{equation}
 c_5=\frac{1-u+\eta-Rs}{1-R}.
 \label{eq:one-side-center-line}
\end{equation}
The hypotheses imply $1/2<c_1,c_5<1$: for example
$u>\delta$ gives $c_1>1/(1+S)>1/2$, and
$\gamma<u-\delta<R-\delta=RS/(1+S)<1/2$ gives $c_5>1/2$.
Thus the four high-radial labels of
Proposition~\ref{prop:capped-demand-map} are exhaustive.

\smallskip\noindent
\emph{Right low labels.}
If the right label is $T_-$, its exact frontier equation gives
$(u+\widehat b_1)^2=1-R+R^2=S^2$, so $\widehat b_1=S-u$.  For a right $L$ label write
$\widehat b_1=kc_1$, $0\le k\le1/2$, and $C=1-k+k^2=c_1^2$.  With $X_R=R+k$, the
Cell-$L$ selector factors as
\[
 q=c_1^2(X_R-1)G_k(X_R),\qquad
 G_k(X)=CX^3+CX^2-k(1-k)X+k^2.
\]
For $X\ge k$, $G_k(X)>0$: when $k>0$,
$G_k'(X)\ge k(1+2k-k^2+3k^3)>0$ and
$G_k(k)=k^2(1+k+k^3)>0$.  Hence $q\le0$ gives $X_R\le1$.  If
$h_R=1-X_R$, then
\[
 S^2-(u+\widehat b_1)^2=h_R(1+2k^2+k(1-k)h_R)\ge0.
\]
Consequently either right low label satisfies
\begin{equation}
 \widehat b_1\le X:=S-u.
 \label{eq:one-side-right-low}
\end{equation}

\smallskip\noindent
\emph{A left low label against right high or Full.}
For left $T_-$ put $z=s/c_5=1-p$ and
$h=\sqrt{1-p+p^2}$.  The component selector gives
$0\le p\le1/2$, the frontier gives $s+\widehat b_5=h$, and its selector gives
$s\le(1-p)h$.  Equation \eqref{eq:one-side-center-line} becomes
$c_5(1-Rp)=1-u+\eta$, whence
\[
 u\ge \eta+(1-h)+Rph.
\]
Put $q_0=ph$.  If $q_0>R$, then
$p(1-p)>R(1-R)$ and the preceding lower bound would give $u>R$.
Thus $q_0\le R$, and
\[
 \eta+1-h>
 \frac{R(1-R)+p(1-p)}2\ge(1-R)q_0.
\]
Substitution in the exact formula
\[
 w=\frac{(1-R)(1-u)p-\eta(1-p)}{1-Rp}
\]
now gives $w<1-h$.  A right high output has the form $H-u$, where
$H=\sqrt{1-\beta+\beta^2}\le1$; for Full take $H=1$.  Hence
\[
 \widehat b_5+\widehat b_1=h+H-(s+u)=1+w-(1-h)-(1-H)<1.
\]

For a left $L$ label write
\[
 c_5=h(x):=\sqrt{1-x+x^2},\qquad
 \widehat b_5=xh(x),\qquad 0\le x\le\frac12,
\]
and, along the center line,
\[
 s(x)=\frac{R-u+\eta+(1-R)(1-h(x))}{R}.
\]
If $y=s(x)/h(x)$, the exact selector factorization is
\[
 \frac{q}{h(x)^2}=(y-(1-x))P_x(y),
\]
where
\begin{align*}
 P_x(y)={}&(1-x+x^2)y^3+(1+2x-2x^2+3x^3)y^2\\
 &+(x+2x^2-x^3+3x^4)y+(x^2+x^3+x^5).
\end{align*}
Every coefficient is nonnegative on $0\le x\le1/2$, and the polynomial is
positive at every nondegenerate point.  Thus a selected $L$ point has
$s(x)\le(1-x)h(x)$.  The two curves meet once in $(0,1/2)$: at $x=0$ the
left side is smaller, while at $x=1/2$ it is enough to use
\[
 u\le\frac{R}{1+R}\quad(\mathrm{Full}),\qquad
 u\le\min\{RS,S/2\}\quad(T_+^{\rm hi}).
\]
Writing $e_0=1-\sqrt3/2$, the corresponding endpoint differences are
\[
 \frac{(1-R)(R^2+2Re_0+2e_0)}{2(1+R)}>0
\]
for Full, and respectively
$[2e_0(1-R)-R^3]/2\ge0$ for $R\le1/2$ and
$(1-R)(3R+4e_0-2)/4\ge0$ for $R\ge1/2$ in the high case.
At the unique transition $x_0$, the $L$ frontier is the $q=0$ endpoint of
the preceding $T_-$ branch.  Since $xh(x)$ increases, every selected left
$L$ output is no larger than that transition output.  The preceding strict
loss therefore also covers $(L,T_+^{\rm hi})$ and $(L,\mathrm{Full})$.

\smallskip\noindent
\emph{Full and high exclusions.}
Left Full forces $s<1/2$ and $\gamma\ge s$.  Right Full or right high gives
$u\le1/2$, but
\[
 \gamma-s=2u-1-\delta+\frac{1-2R}{1-R}w<0:
\]
for $R\ge1/2$ this is immediate, while for $R<1/2$ use $w<1-u$ to bound it
by $(u-R)/(1-R)-\delta<0$.  Thus left Full cannot pair with either label.
If the left label is high and the right one Full, then $s<1/2$ and
$u\le R/(1+R)$, whereas $\gamma>0$ and $w>1/2-u$ force
$u>R/2+\eta>R/(1+R)$; the final inequality is equivalent to
$2(1+R)>1+S$.  This pair is also impossible.

\smallskip\noindent
\emph{A right low label.}
Use \eqref{eq:one-side-right-low}.  If $s>X$, the cap gives
$\widehat b_5+\widehat b_1<1$.  Suppose $s\le X$ and put
\[
 c_X=X+2\delta,\qquad f(c,z)=c^4-c^2+zc-z^2.
\]
At the limiting value $u=R$, with $\kappa=\delta$, one has
\[
 X_0=\frac{1-2\kappa}{1+\kappa},\qquad
 c_0=\frac{1+2\kappa^2}{1+\kappa}.
\]
Now $c_0>\sqrt3/2$ because
$16\kappa^4+13\kappa^2-6\kappa+1>0$, and
\[
 f(c_0,X_0)=
 \frac{\kappa^2(1-2\kappa)^2
 (4\kappa^4+4\kappa^3+10\kappa^2+6\kappa+5)}{(1+\kappa)^4}>0.
\]
Along the $u$-line,
$\frac d{du}f(c_X,X)=-4c_X^3+c_X+X<0$, so the same two signs hold before
the limiting endpoint.  Therefore, for
$\ell(c)=c(1-\sqrt{4c^2-3})/2$,
\[
 \ell(c_X)<X<c_X-\ell(c_X),\qquad \ell(c_X)<1-X.
\]

Write $c=h(z)=\sqrt{1-z+z^2}$ and let $z_X$ satisfy $h(z_X)=c_X$.
The actual $c_5(s)$ corresponds to $0<z\le z_X<1/2$, and
\[
 s(z)=s_0+\frac{1-R}{R}(1-h(z)),\qquad
 s_0=\frac{R-u+\eta}{R}>0.
\]
The transition input $(1-z)h(z)$ decreases, and the preceding root ordering
gives $s(z_X)<(1-z_X)h(z_X)$, hence the same strict inequality for all
$z\le z_X$.  To check the order of the two boundary coordinates put
\[
 \phi(z)=s(z)-zh(z),\qquad k_R=\frac{1-R}{R}.
\]
Its endpoint values are $s_0>0$ and $X-\ell(c_X)>0$.  Moreover
\[
 \phi'(z)=\frac{(k_R+z)(1-2z)}{2h(z)}-h(z).
\]
For $k_R\le2$ this is nonpositive; for $k_R>2$ its zero is described by the
strictly increasing function
$K_0(z)=(2-3z+4z^2)/(1-2z)$, so the minimum is again at an endpoint.
Thus $zh(z)<s(z)$.  Applying the already displayed polynomial $P_z$ gives
the strict Cell-$L$ selector, and
$s+zh(z)\le X+\ell(c_X)<1$.  Since
$\partial_bF_L=c(1-2z)>0$ and each feasible fiber is an interval, the capped
maximum is
\[
 \widehat b_5\le zh(z)\le z_Xh(z_X)=\ell(c_X)<1-X.
\]
Together with $\widehat b_1\le X$, this proves the loss for every right low label.

\smallskip\noindent
\emph{High--high.}
Let $c_L(z)$ be the unique root in $[\sqrt3/2,1]$ of $f(c,z)=0$.
With $D_c=4c^3-2c+z>0$, implicit differentiation gives
\[
 c_L''(z)=
 \frac{2(c^2-cz+z^2)+16c^2z(c-z)}{D_c^3}>0.
\]
A selected left high label requires $s<1/2$ and $c_5(s)\le c_L(s)$.
Define
\[
 s_0=\frac{R-u+\eta}{R};
\]
then $0<s_0<s$ and $c_5(s_0)=1$.  The explicitly named function
$g(z)=c_5(z)-c_L(z)$ is concave, with $g(s_0)>0$.  The right high bound
$u\le\min\{RS,S/2\}$ gives $c_5(1/2)>7/8$.  For $R\le1/2$ this follows
after squaring from
$17-10R+9R^2-64R^3-64R^4>0$ (a decreasing polynomial with value $9/4$ at
$1/2$); for $R\ge1/2$ it follows from
$(3+R)^2-16S^2=(1-R)(15R-7)>0$.  Finally
\[
 f(7/8,1/2)=33/4096>0
\]
and $f$ increases in $c$ on this range, so $c_L(1/2)<7/8$ and
$g(1/2)>0$.  Concavity contradicts $g(s)\le0$.  Thus high--high is
impossible.

If both labels are low, the cap already gives
$\widehat b_5+\widehat b_1\le s+u=1-w<1$.  The preceding five paragraphs cover every other
ordered pair of the four labels, proving \eqref{eq:one-side-loss}.
\end{proof}

\begin{lemma}[CE2 two-endpoint capped loss]
\label{lem:two-endpoint-capped-loss}
Let $[x,U]$ and $[y,v]$ be an exact CE2 pair as in
Proposition~\ref{prop:center-exact-formulas}.  Put
\[
 p=1-U,\qquad q=1-v,\qquad
 r=\frac{x}{x+y},\qquad w=\frac{y}{x+y},
\]
and reflect if necessary so that $0<w\le1/2$ and $r=1-w$.  Then
\begin{equation}
 F_{p/w}(p)+F_{q/r}(q)<1.
 \label{eq:two-endpoint-loss}
\end{equation}
\end{lemma}

\begin{proof}
Put
\[
 S_0=x+y,\quad K=\sqrt{1-wr},\quad
 z=\frac{w}{1+K},\quad\zeta=\frac{r}{1+K},
 \quad\alpha=\frac pw,\quad\beta=\frac qr.
\]
Then $D=S_0K$, $1-K=wr/(1+K)$, and the exact midpoint inequalities give
$1/2<\alpha,\beta<1$.  Dividing the coupling equation
$(U+v)S_0-xy=D$ by $S_0$, and using successively $x<U$ and $y<v$, gives
the strict endpoint inequalities
\begin{equation}
 \beta+p>1+z,\qquad \alpha+q>1+\zeta.
 \label{eq:ce2-strict-endpoints}
\end{equation}
Define
\[
 \Phi_w(\alpha)=F_\alpha(w\alpha),\qquad
 \Phi_r(\beta)=F_\beta(r\beta),\qquad
 h(t)=\sqrt{1-t+t^2}.
\]
Thus the desired sum is $\Phi_w(\alpha)+\Phi_r(\beta)$.

\smallskip\noindent
\emph{Selected branch parametrizations.}
For a side of weight $\sigma\in\{w,r\}$, every $L$ label has
\begin{equation}
 c=h(k),\qquad F_c(\sigma c)=kh(k),\qquad0\le k\le w,
 \label{eq:two-endpoint-L-param}
\end{equation}
on either side.  On the large side the range follows from
\[
 Q_{\rm cell}/h(k)^2=(k-w)G_k(r+k),
\]
where
$G_k(X)=h(k)^2X^3+h(k)^2X^2-k(1-k)X+k^2>0$ for $X\ge k$.
The remaining selected parametrizations are
\begin{align}
 \alpha&=\frac{h(a)}{w+a},&
 \Phi_w(\alpha)&=a\alpha,& r\le a<1,
 \label{eq:two-endpoint-small-high}\\
 \beta&=\frac{h(b)}{r+b},&
 \Phi_r(\beta)&=b\beta,& r\le b<1,
 \label{eq:two-endpoint-large-high}\\
 \beta&=\frac K{r+t},&
 \Phi_r(\beta)&=t\beta=K-r\beta,& w\le t\le r.
 \label{eq:two-endpoint-large-tminus}
\end{align}
For example, the small-high selector factors as
\[
 h(a)^2a\left(\frac{w}{(w+a)^2}-(1-a)\right),\qquad
 w-(1-a)(w+a)^2=(a-r)(a^2+wa-w),
\]
which gives $a\ge r$; the other two factorizations are
$(b-w)(b^2+rb-r)$ and $(t-w)(r^2-wt)$, respectively.  These formulas
specify the selected geometric components, not discarded algebraic roots.

The small-side $T_-$ label is absent for $w<1/2$.  Large-side Full is
incompatible with the first inequality in
\eqref{eq:ce2-strict-endpoints}.  Small-side Full can pair only with $L$:
either high or $T_-$ on the large side has $\beta\le K$, which would force
$p>(1+r)z>w/(1+w)$, contrary to Full.  Thus, up to the symmetric
$w=r=1/2$ tie, the exact list is
\begin{equation}
 (\mathrm{Full},L),(T_+^{\rm hi},L),(L,L),(L,T_-),
 (L,T_+^{\rm hi}),(T_+^{\rm hi},T_-),(T_+^{\rm hi},T_+^{\rm hi}).
 \label{eq:two-endpoint-pairs}
\end{equation}

Low--low sums are at most $K<1$: an $L$ output is at most $wK$, while
\eqref{eq:two-endpoint-large-tminus} is at most $rK$.  For Full--$L$, put
\[
 b_{\rm thr}=1+z-\frac{w}{1+w},\qquad
 \kappa=\frac{w}{1+(1+w)z}.
\]
Full and \eqref{eq:ce2-strict-endpoints} give $\beta>b_{\rm thr}$ and
$(1+\kappa)b_{\rm thr}=1+z$.  Direct reduction yields
\[
 b_{\rm thr}^2-h(\kappa)^2
 =\frac{w^2(A(w)+KC(w))}{D_0(w,K)}>0,
\]
where
\begin{align*}
 A(w)&=8-5w+22w^2+6w^3+5w^4+5w^5-w^6,\\
 C(w)&=8-w+14w^2+4w^3-2w^4+w^5,\\
 D_0(w,K)&=((1+w)(1+K))^2(1+K+w+w^2)^2.
\end{align*}
Both numerator polynomials are positive on $[0,1/2]$.  Since $h$ decreases
and $(1+k)h(k)$ increases there,
$\beta=h(k)>b_{\rm thr}>h(\kappa)$ implies
$(1+k)\beta<1+z$; combined with \eqref{eq:ce2-strict-endpoints}, this gives
$k\beta<p$ and hence the strict Full--$L$ loss.

It remains to verify the four pairs containing a high label on the small
side.

\smallskip\noindent
\emph{$(L,T_+^{\rm hi})$.}
Use parameters $0\le k\le w$ and $r\le t<1$:
\[
 \alpha=h(k),\quad\Phi_w=kh(k),\qquad
 \beta=\frac{h(t)}{r+t},\quad\Phi_r=\frac{th(t)}{r+t}.
\]
The first output and the last output increase in their parameters, while
$h(t)/(r+t)$ decreases.  If $w\le2/5$, then
\[
 \Phi_w+\Phi_r<wK+\frac1{2-w}<1;
\]
after using $K\le1-wr/2$, the positive cleared gap is
$P(w)=w^4-3w^3+4w^2-6w+2$, which decreases on $[0,2/5]$ and has
$P(2/5)=46/625$.  If $w\ge2/5$, the first endpoint inequality gives
$\beta>r+z\ge3/4$.  Since
$h(3/4)/(r+3/4)=\sqrt{13}/(7-4w)<3/4$, monotonicity forces $t<3/4$.
Therefore
\[
 \Phi_w+\Phi_r<\frac{\sqrt3}{4}+\frac{3\sqrt{13}}{20}<1.
\]

\smallskip\noindent
\emph{$(T_+^{\rm hi},T_-)$.}
Use $a,t$ from \eqref{eq:two-endpoint-small-high} and
\eqref{eq:two-endpoint-large-tminus}.  Both demands are at most $K$.
The first endpoint inequality gives
\[
 \alpha>\frac{1+z-K}{w}=\frac{1+r}{1+K}=:a_0.
\]
Thus $K>1-w^2$, which forces $w>1/3$, and comparison at $a=2/3$ forces
$a<2/3$.  The function
\[
 G(a)=\frac{(1+a)h(a)}{w+a}
\]
decreases on $[r,2/3]$, because its derivative numerator
$2a^3+(4w-1)a^2+(1-w)a+w-2$ is at most its value
$-7/54$ at $(2/3,1/2)$.  Hence $G(a)\le(1+r)K$.
Using the second endpoint inequality and
$\Phi_r=K-r\beta$ gives
\[
 \Phi_w+\Phi_r<(2+r)K-1-\zeta<1.
\]
After multiplication by $1+K$, the last positive gap is
$r(3w-w^2-K)$; its squared comparison is
\[
 (3w-w^2)^2-K^2=w^4-6w^3+8w^2+w-1>0
\]
for $w>1/3$ (value $1/81$ at $1/3$, positive derivative thereafter).

\smallskip\noindent
\emph{$(T_+^{\rm hi},T_+^{\rm hi})$.}
Use parameters $a,b$ from \eqref{eq:two-endpoint-small-high}--
\eqref{eq:two-endpoint-large-high}.  The endpoint inequalities first force
$w>2/5$: for $w\le2/5$, the asserted contrary inequality
$K(w+1/(2r))\le1+z$ reduces, after multiplication by $2r(1+K)$, to
\[
 K(2w^2-4w+1)+2w^4-4w^3+w^2-w+1>0,
\]
which is immediate according as the coefficient of $K$ is nonnegative or,
using $K\le1$, from the decreasing polynomial
$2w^4-4w^3+3w^2-5w+2\ge172/625$.

For $F_c(t)=(1+t)h(t)/(c+t)$, the derivative numerator
$2t^3+(4c-1)t^2+(1-c)t+c-2$ is increasing on the present rectangle, so
$F_c$ has at most one interior minimum.  Endpoint comparison gives
\[
 \Phi_w+\alpha\le\frac2{1+w},\qquad
 \Phi_r+\beta\le\frac2{1+r}.
\]
The nontrivial endpoint signs are exactly
\[
 4-(1+r)^2(1+w)^2K^2
 =-w^2(w-1)^2(w^2-w-3)>0
\]
and
\[
 16r^2-(1+r)^4h(r)^2
 =(1-r)(r^5+4r^4+7r^3+9r^2-4r-1)>0;
\]
the bracket is increasing on $[1/2,1]$ and equals $13/32$ at $1/2$.
Weighting the two strict endpoint inequalities by $w/K^2$ and $r/K^2$
gives
\[
 \alpha+\beta>\frac{2K+1}{K(1+K)}.
\]
Consequently
\[
 \Phi_w+\Phi_r<\frac2{1+w}+\frac2{1+r}
 -\frac{2K+1}{K(1+K)}<1.
\]
The numerator of the last gap is $3Kwr-Q(w)$, where
$Q(w)=w^4-2w^3+7w^2-6w+2>0$.  Its squared difference is
\[
 D(w)=-w^8+4w^7-9w^6+13w^5-41w^4+65w^3-55w^2+24w-4.
\]
Here $D'(w)=(1-2w)H(w)$ with
\[
 H(w)=4w^6-12w^5+21w^4-22w^3+71w^2-62w+24>0
\]
on $[2/5,1/2]$; use
$71w^2-62w+24\ge743/71$ and the remaining cubic block at least $-11/4$.
Thus $D$ increases and $D(2/5)=4904/390625>0$, proving the claim.

\smallskip\noindent
\emph{$(T_+^{\rm hi},L)$.}
Use the fully specified parameters
\[
 \alpha=\frac{h(t)}{w+t},\quad p=w\alpha,\quad b=t\alpha,
 \quad\frac12\le t<1,
\]
and
\[
 \beta=H=h(k),\quad \widehat b_L=kH,\quad 0\le k\le w.
\]
Since $p+b=h(t)$, the first endpoint inequality gives
\begin{equation}
 1-(b+kH)>G:=2+z-h(t)-(1+k)H.
 \label{eq:two-endpoint-high-L-G}
\end{equation}
Put
\[
 p_0=1+z-K=\frac{w(2-w)}{1+K},
\]
let $t_0\in(1/2,1)$ be the unique point with
$p(t_0)=wh(t_0)/(w+t_0)=p_0$, and put $b_0=t_0p_0/w$.
The exact endpoint lemma is
\begin{equation}
 b_0<1-wK.
 \label{eq:two-endpoint-b0}
\end{equation}
To verify it, set $b_*=1-wK$ and $T_*=wb_*/p_0$.  One has $0<T_*<1$, and
\[
 p_0^2(w+T_*)^2-w^2h(T_*)^2
 =-\frac{w^3(KE(w)+J(w))}{(1+K)^2(2-w)^2}>0,
\]
where
\[
 E(w)=2w^5+3w^3-20w^2+23w-6,
\]
\[
 J(w)=w^6+8w^5-22w^4+12w^3+6w^2+2w-6.
\]
Here $J\le-111/64$; if $E>0$, then
$KE+J<E+J<0$, because $E+J$ is increasing and equals $-139/64$ at
$w=1/2$.  Thus $p(T_*)<p(t_0)$.  Since $p(t)$ decreases,
$t_0<T_*$ and \eqref{eq:two-endpoint-b0} follows.

Finally put $P=1+z-p$.  If $P<K$, then $t<t_0$ and $k\le w$, so
\[
 G>2+z-h(t_0)-(1+w)K=1-b_0-wK>0.
\]
If $P\ge K$, then $K\le P\le P_1:=1+z-w/(1+w)\le1$ and there is
$a\in[0,w]$ with $h(a)=P$.  Since $P<H$, one has $k<a$ and
$(1+k)H<(1+a)P=P+\ell(P)$, where
$\ell(P)=P(1-\sqrt{4P^2-3})/2$.  Hence
\[
 G>\mathcal D(P):=1-b(P)-\ell(P).
\]
This function is concave.  Indeed $\ell''(P)>0$, and the high output $b$ is
convex in $p=1+z-P$: with
$A_t=2+w-(1+2w)t>0$ and
$Q_t=8wt^2+4t^2-8wt-13t-w+4<0$,
\[
 \frac{d^2b}{dp^2}=-\frac{2h(t)(t+w)^3Q_t}{w^2A_t^3}>0.
\]
At $P=K$, \eqref{eq:two-endpoint-b0} gives
$\mathcal D(K)=1-b_0-wK>0$.  At $P=P_1$, set
$\kappa=w/(1+(1+w)z)$.  The Full--$L$ comparison already proved gives
$P_1>h(\kappa)$, hence
$\ell(P_1)<\kappa P_1=w/(1+w)$, while $b(P_1)=1/(1+w)$.
Thus $\mathcal D(P_1)>0$, and concavity gives $G>0$ throughout.
Equation \eqref{eq:two-endpoint-high-L-G} proves the final hard pair.

The exact list \eqref{eq:two-endpoint-pairs} is now exhausted, proving
\eqref{eq:two-endpoint-loss}.
\end{proof}

\subsection{The exactly-one-Vd1/Vd2 placements}

We now assume CE2, $N_+=1$, and exactly one row is Vd1 or Vd2.  The corner
normal form of Proposition~\ref{prop:vd-corner-normal-form} will be used in
the following form: for some $t>0$ and $d=\sqrt{t^2+t+1}$,
\begin{equation}
 x-(t+1)y\le a,\qquad ty-(t+1)x\le tb,\qquad
 tx+y\le d-a-tb.
 \label{eq:vd-corner-form}
\end{equation}
In particular $a+b<1/2$ for a positive-support row.

\begin{lemma}[Vd1 adjacent rescue]
\label{lem:vd1-adjacent-rescue}
Assume an original open-role skeleton cover in the CE2 exact-$M_0$ branch,
with $T_C\cap\{M_0,\ldots,M_5\}=\{M_0\}$.  Suppose $T_0$ is the unique Vd1
row, $M_1\in T_0$, $T_1$ is uniquely supercritical, and
$T_2,\ldots,T_5$ are nonsupercritical Vd0 rows.  Suppose also that these are
the only positive-adjacent-support roles.  Then the roles do not cover the
perimeter together with $r_1$.
\end{lemma}

\begin{proof}
From \eqref{eq:vd-corner-form}, the $r_1$ interval is
\[
 [c,u],\qquad c=\frac{t(1-b)}{t+1},\qquad
 u=\frac{d-a-tb-1}{t}.
\]
The midpoint inequalities and absence of positive $r_5$ support force
$t\ge1$.  They also give
\[
 a\le F(t,c):=d-1-\frac{3t}{2}+c(t+1)
 \le L(c):=\sqrt3-\frac52+2c.
\]
With $A(c)=1-\mathcal B(c)$, squaring positive sides gives
\[
 2L(c)\le A(c),
\]
because the difference is
$4(20c^2+(18\sqrt3-52)c+47-24\sqrt3)>0$ on $[0,1/2]$.
Writing $\delta=1-u$, the same normal form yields
\[
 \frac{a}{a+\delta}\le\frac{L(c)}{L(c)+1/2}\le2L(c)\le A(c).
 \label{eq:vd1-auxiliary}
\]
Thus $a\le A(c)$.  If the CE2 interval on $e_{5,0}$ hides the gap after
$T_0$, its side parameters $X,Y,\lambda,\rho$ satisfy
$Y\ge\lambda\delta$ and $S\le a$, whence
\[
 T=X+\lambda\le a+\lambda(u-a)\le\frac{a}{a+\delta}\le A(c).
\]
In every other ordering its forced tail starts no later than $a$.
Consequently the far-row reach is always $h\ge\mathcal B(c)$.

Coverage of $r_1$ gives the supercritical row a radial demand at least $c$.
Therefore Lemma~\ref{lem:free-supercritical-envelope} gives
$b_1<\mathcal B(c)\le h$.  The four remaining row caps would then have to
satisfy
\[
 \sum_{i=2}^5(a_i+b_i)\ge(1-b_1)+1+1+1+h>4,
\]
a contradiction.
\end{proof}

\begin{lemma}[Adjacent positive-support placement]
\label{lem:vd-adjacent-placement}
Assume an original open-role skeleton cover in the CE2 exact-$M_0$ branch,
with $T_C\cap\{M_0,\ldots,M_5\}=\{M_0\}$.  Suppose $T_0$ is uniquely
supercritical, $T_1$ is the unique Vd1/Vd2 row, and
$T_2,T_3,T_4,T_5$ are nonsupercritical Vd0 rows; in particular, there is no
additional positive-adjacent-support row.  Then the perimeter together with
$r_1,r_2$ is not covered.  The reflected $T_5$ placement is also impossible.
\end{lemma}

\begin{proof}
Use the CE2 variables $S=x+y$, $D=\sqrt{x^2+xy+y^2}$ and $E=vS-y$.
The center length on $r_2$, measured from $O$, is $d_2^C=E/S$.  Let $A,H$
be the boundary demands forced on $T_1$ from $e_{0,1}$ and the propagated
$e_{5,0}$ tail.  The corner cap gives
\begin{equation}
 A+H<\frac12.
 \label{eq:adjacent-AH}
\end{equation}
The exact radial envelope of Proposition~\ref{prop:exact-admissible-set},
including the Cell-$T$ selector $c\le2M$, gives
\begin{equation}
 c_{\max}\left(\frac12+A,H\right)\le1-\frac H3.
 \label{eq:adjacent-envelope}
\end{equation}
For completeness, at $c=1-H/3$ the Cell-$L$ polynomial is
\[
 \frac{H}{81}(H^3-12H^2-63H+27)>0
 \quad(0<H\le3/8),
\]
while the Cell-$T$ expression is increasing in the larger boundary input
$p\in[1/2,1-H]$; at the order-change point it is nonnegative, and if the
cell is already active at $p=1/2$ its endpoint sign is
$H^4-5H^3+9H^2/4+12H-9/2>0$.  Also $1-H/3\le2p$, so the selected, rather
than discarded, component is used.  This proves \eqref{eq:adjacent-envelope}.

The CE2 coupling and \eqref{eq:adjacent-AH} give the strict outer ratio
\begin{equation}
 d_2^C<\frac H3.
 \label{eq:adjacent-outer-ratio}
\end{equation}
There are two endpoint sources for $H$.  If $H=1-u$, put
$K=x+2y-xy-D$; then $d_2^C/H=1-K/(SH)$, and the diameter endpoint bounds
give $K/(SH)>2/3$.  If $H=1-a_0$, the disk inequality gives
$H\ge L(y)=(2+y-\sqrt{4-3y^2})/2$; squaring the CE2 comparison yields
$(D+xy-x-y)/S<L(y)/3\le H/3$.  These are precisely the two alternatives,
proving \eqref{eq:adjacent-outer-ratio}.

Now $r_2$ can be covered only by $T_2$, the center, and a possible bridge
from $T_1$.  The normal form makes a bridge imply $H<d_2^C$, contrary to
\eqref{eq:adjacent-outer-ratio}.  Without a bridge, boundary propagation
gives $T_2$ inputs strictly exceeding $1/2+A$ and $H$; then
\eqref{eq:adjacent-envelope} gives
$c_2\le1-H/3<1-d_2^C$, so $T_2$ cannot meet the center interval either.
\end{proof}

\begin{lemma}[Nonadjacent positive-support placements]
\label{lem:vd-nonadjacent-placement}
Assume an original open-role skeleton cover in the CE2 exact-$M_0$ branch,
with $T_C\cap\{M_0,\ldots,M_5\}=\{M_0\}$.  Suppose $T_0$ is uniquely
supercritical, $T_\tau$ is the unique Vd1/Vd2 row for
$\tau\in\{2,3,4\}$, and every other vertex row is nonsupercritical Vd0;
in particular, there is no additional positive-adjacent-support row.  Then
the perimeter together with $r_\tau$ is not covered.
\end{lemma}

\begin{proof}
Let $A,H$ be the two boundary demands propagated to $T_\tau$, and put
$B=1-A$, $U=1-H$.  The distance endpoint
\[
 \beta(z)=\frac{-z+\sqrt{4-3z^2}}2
\]
gives $B\le\beta(x)$ and $U\le\beta(y)$, whether an extent comes from the
supercritical row or from the corresponding CE2 endpoint.  The exact CE2
comparison
\begin{equation}
 \frac{D+xy}{S}+\beta(x)<2
 \label{eq:ce2-extent-comparison}
\end{equation}
follows by squaring: with $b=\beta(x)$, the required quadratic in $y$ is
concave, positive at $y=0$, and at $y=1$ its numerator reduces to
$4x^2(x^4+4x^3+9x^2+11x+8)$.  Reflection gives the $y$ version.  Since
$u+v=(D+xy)/S$, it follows that
\begin{equation}
 u+v-1<\min(A,H)=:m.
 \label{eq:nonadjacent-margin}
\end{equation}

Put $P=vS-y$ and $Q=uS-x$.  Then $P+Q=(u+v-1)S$, while the center lengths
on $r_2,r_3,r_4$ are
\[
 \frac P S,\qquad \min\left\{\frac P y,\frac Q x\right\},
 \qquad\frac Q S.
\]
Equation \eqref{eq:nonadjacent-margin} makes each strictly less than $m$.
On the other hand \eqref{eq:vd-corner-form} gives
$c_\tau<1-m$.  Hence the vertex-side demand $1-d_\tau^C$ is strictly larger
than $c_\tau$, leaving $r_\tau$ uncovered.
\end{proof}

\begin{lemma}[Vd1--supercritical replacement]
\label{lem:vd1-pair-replacement}
\leavevmode\par\noindent
Assume an original open-role perimeter-and-radial-skeleton cover in the CE2
exact-$M_0$ branch and the complementary no-additional-positive-support
case.  Let $T_i$, $i\ne0$, be uniquely supercritical, and let the unique Vd1
row, distinct from $T_0$ and adjacent to $T_i$, contain $M_i$.  Assume every
other vertex row is nonsupercritical Vd0 and the center has no boundary trace
on the shared edge of this pair.  Then the pair can be replaced by two open
nonsupercritical Vd0 roles preserving all boundary and radial demands used
by Proposition~\ref{prop:nplus-zero-all-vd0}.
\end{lemma}

\begin{proof}
Normalize the Vd1 row at $V_0$ and the supercritical row at $V_1$.
By the shared-edge hypothesis, no center trace intervenes on $e_{0,1}$;
by the no-additional-positive-support hypothesis, no third vertex role has
positive boundary or radial support in the handoffs used below.
In \eqref{eq:vd-corner-form}, midpoint rescue and one-sided support imply
$t\ge1$ and, with
\[
 c=\frac{d-a-tb}{t+1},\quad
 \lambda=\frac{t(1-b)}{t+1},\quad
 \mu=\frac{d-a-tb-1}{t},
\]
give the strict consequences
\begin{equation}
 a+c<1,\qquad a<\lambda\le\frac12,\qquad
 b<\frac12,\qquad \mu<1-a.
 \label{eq:replacement-margins}
\end{equation}
The shared edge forces the supercritical input $a_i\ge1-b>1/2$, and radial
coverage forces $c_i\ge\lambda$.  A direct consequence of
Proposition~\ref{prop:exact-admissible-set} is
\[
 (x,y,z)\in\mathcal A,\quad x\ge1/2,\quad z\le1/2
 \quad\Longrightarrow\quad y\le1-z.
\]
Indeed, substituting $x=1/2,y=1-z$ in the selected supercritical polynomial
gives $z^2(2z-5)(2z-1)/4\ge0$, and the polynomial is increasing in both
relevant coordinates.  Hence $b_i\le1-c_i\le1-\lambda$ and
$a+b_i<1$.  Open radial handoff further gives
\[
 c_i^{\rm req}<\max\{c_i,\mu\}
 <\max\{1-b_i,1-a\}.
\]

Choose $a<p_1<p_2<1-b_i$ within these strict margins.  In local coordinates
use the unit triangles
\[
 \Delta_p^-=\conv\{(0,1-p),(1,1-p),(0,-p)\},\quad p\le1/2,
\]
and
\[
 \Delta_p^+=\conv\{(p,0),(p,1),(p-1,0)\},\quad p\ge1/2.
\]
Their incident reaches are $p,1-p$, their own-radial reach is respectively
$1-p,p$, and they have zero adjacent support.  Small translations, chosen
below every strict margin above, make the two replacements open Vd0 roles
with boundary sum $<1$ while preserving the shared boundary and both radial
handoffs.  Thus the datum reduces to Proposition~\ref{prop:nplus-zero-all-vd0}.
\end{proof}

\begin{proposition}[Complementary exact Vd1/Vd2 placements]
\label{prop:ce2-one-vd-placement}
Consider the CE2 exact-$M_0$, $N_+=1$ branch with exactly one Vd1 or Vd2
role.  Assume that no other vertex row has positive adjacent support and that
the unique Vd2 role, if present, covers neither neighboring midpoint.  Then
the configuration is impossible.
\end{proposition}

\begin{proof}
By the vertex classification, the no-additional-positive-support hypothesis
makes every vertex row other than the unique Vd1/Vd2 row Vd0; all such rows
other than the unique supercritical row are nonsupercritical.  This is
precisely the complementary branch in which Lemmas
\ref{lem:vd1-adjacent-rescue}--\ref{lem:vd1-pair-replacement} apply.

Let $T_\sigma$ be uniquely supercritical and $T_\tau$ the unique Vd1/Vd2
row.  They are distinct by the corner cap.  If $\sigma=0$, the adjacent
placements $\tau=1,5$ are excluded by
Lemma~\ref{lem:vd-adjacent-placement}, and $\tau=2,3,4$ by
Lemma~\ref{lem:vd-nonadjacent-placement}.  If $\tau=0$, midpoint forcing
makes $\sigma=1$ or $5$ and $T_0$ cover that midpoint.  Vd1 is excluded by
Lemma~\ref{lem:vd1-adjacent-rescue}; Vd2 would cover the neighboring midpoint
$M_\sigma$, contrary to the proposition's hypothesis.

If neither index is zero, midpoint forcing makes the two rows adjacent and
the positive-support row rescue the supercritical midpoint.  Vd2 is again
excluded by the neighboring-midpoint hypothesis; Vd1 reduces by
Lemma~\ref{lem:vd1-pair-replacement} to the $N_+=0$ all-Vd0 obstruction.
These alternatives exhaust the complementary exact-placement branch.
\end{proof}

\subsection{Strategy 2 terminal routing}

\begin{proposition}[Exact-demand terminal branches]
\label{prop:demand-branches}
The exact-demand method proves the following terminal exclusions:
\begin{enumerate}
\item CE1 or CE2, $N_+=0$, all vertex roles Vd0;
\item CE1 or CE2, $N_+=0$, with at least one T3-like role and no Vd1/Vd2;
\item CE1 or CE2, $N_+=1$, all vertex roles Vd0, with at least one boundary
gap;
\item CE1 or CE2, $N_+=1$, exactly one T3-like role and no Vd1/Vd2;
\item the complementary exact-placement subcases of CE2, $N_+=1$, with
exactly one Vd1 or Vd2: no additional positive-support row and no Vd2
neighboring-midpoint rescue.
\end{enumerate}
All gap alternatives include singleton gaps.
\end{proposition}

\begin{proof}
The five items are respectively Propositions
\ref{prop:nplus-zero-all-vd0}, \ref{prop:nplus-zero-t3},
\ref{prop:nplus-one-all-vd0}, \ref{prop:nplus-one-one-t3}, and
\ref{prop:ce2-one-vd-placement}.  The strictness at open handoffs appears in
the weak endpoint bounds, the nonattained supercritical envelope, and the
strict replacement margins; no positive-length assumption is made about a
V-gap itself.
\end{proof}
