\subsection{Strategy 2: exact boundary--radial demand propagation}
\label{subsec:exact-demand-guide}

Length alone does not record where a trace must continue.  Strategy~2 keeps
that positional information.  In local unit vectors
\[
 u=\left(\frac12,\frac{\sqrt3}{2}\right),\qquad
 v=\left(\frac12,-\frac{\sqrt3}{2}\right),
\]
define
\[
 K(a,b,c)=\conv\{0,au,bv,c(u+v)\}.
\]
Let $B_c(a)$ be the largest outgoing demand $b$ for which $K(a,b,c)$ fits
in a closed unit equilateral triangle, and set
\[
 F_c(a)=\min\{B_c(a),1-a\},\qquad G_c(a)=1-F_c(a).
\]
The admissible set is coordinatewise down-closed.  Hence $F_c$ is
nonincreasing, $G_c$ is nondecreasing and extensive, and reflection gives
an exact duality.  The piecewise formula has a genuine downward jump; no
argument below uses continuity at that jump.

\subsubsection{How an actual row propagates a demand}

Suppose an actual nonsupercritical row has $A_i\ge z$, radial reach
$C_i\ge c_i$, and $A_i+B_i\le1$.  Then its realized demand triple gives
\[
 B_i\le F_{c_i}(z).
\]
If the next incident open traces cover their boundary point, the next actual
incoming reach satisfies
\begin{equation}
 A_{i+1}\ge1-B_i\ge G_{c_i}(z).
 \label{eq:actual-propagation}
\end{equation}
Thus each successive use of \eqref{eq:actual-propagation} is an inequality
for an actual row, not merely a formal composition of scalar functions.

For a CE1 center trace, exact center geometry supplies one interval
$[s,t]\subset e_{0,1}$ and six exits $d_i$ from $O$; the complementary
radial demand is $c_i=1-d_i$.  For CE2 there are coupled intervals
$[x,u]\subset e_{5,0}$ and $[y,v]\subset e_{0,1}$.
Figure~\ref{fig:ce1-ce2-n0-all-vd0} in
Section~\ref{sec:cyclic-all-vd0} gives a common schematic for the
CE1/CE2, $N_+=0$, all-Vd0 package.  It shows only three representative Vd0
roles; the argument treats all six.

\subsubsection{The branch-level contradictions}

For a one-gap branch, repeated use of \eqref{eq:actual-propagation} gives the
five actual-row chain $1\to2\to3\to4\to5\to0$.  The exact terminal estimates
proved in Section~\ref{sec:cyclic-all-vd0} have the forms
\[
 A_0\ge Z>B_{c_0}(s)\ge A_0
\]
for CE1 and
\[
 A_0>Z_R>B_{c_0}(y)\ge A_0
\]
for the CE2 right gap.  Reflection $i\mapsto-i$ gives the fully written left
chain $5\to4\to3\to2\to1\to0$ and
\[
 B_0>Z_L>B_{c_0}(x)\ge B_0.
\]
The two-gap CE2 state uses the exact two-endpoint capped loss; the no-active-
gap $N_+=0$ state uses the strict overlap of a finite relatively open cover
of the connected boundary circle.  The remaining Strategy~2 branches use the
same interface together with the T3-like side tradeoff or the exact
Vd1/Vd2 placement classification.

All radical comparisons, low-root bounds, four-label branch tables, capped
loss inequalities, and placement polynomials are proved in
Sections~\ref{sec:exact-local-demand-calculus}--%
\ref{sec:t3-vd-demand-branches}.  In particular,
the half-edge rational envelope is used only on its valid domain
\[
 p\ge\frac12,\qquad0\le h\le p,\qquad p+h<1;
\]
Subsection~\ref{sec:half-edge-envelope} also records a counterexample outside
that domain.

\paragraph{Branches closed by exact demand.}
Sections~\ref{sec:cyclic-all-vd0} and
\ref{sec:t3-vd-demand-branches} close every row of Table~\ref{tab:routing}
assigned to route $2$, including the complementary exact placements in the
hybrid $1+2$ row.  The terminal list in
Proposition~\ref{prop:demand-branches} consists of the all-Vd0 and T3-like
$N_+=0$ packages, every positive-gap all-Vd0 state with $N_+=1$, the
exactly-one-T3-like state, and those complementary CE2 placements.  Singleton
gaps are included.  Equation~\eqref{eq:actual-propagation} is the handoff from
each scalar inequality to the actual role geometry.
