\section{Rational and monotonicity bounds}
\label{app:rational-monotonicity}

The adjacent CE2 placement in Appendix~\ref{app:strategy2-details} uses a
rational upper bound for a single admissible-set fiber.  We isolate it here
because the domain restriction is
essential and because the same formula is false on the full nonsupercritical
fiber domain.

\begin{lemma}[Half-edge rational radial envelope]
\label{lem:half-edge-radial-envelope}
Suppose
\[
 \frac12\le p<1,\qquad 0\le h\le p,\qquad p+h<1.
\]
Then
\begin{equation}
 c_{\max}(p,h)\le1-\frac h3.
 \label{eq:half-edge-radial-envelope}
\end{equation}
The inequality is strict when the selected admissible-set component is
$\mathcal A_T$.
\end{lemma}

\begin{proof}
Put
\[
 s=p+h,\qquad d=p^2+ph+h^2,\qquad q=s^4-s^2+ph.
\]
Because $s<1$, one has $d=s^2-ph<1$, so only the two nonsupercritical cells
of Proposition~\ref{prop:exact-admissible-set} occur.  Since $p\ge h$, in
$\mathcal A_L$ the selected radial value is the unique root
$C_L(h)\in[\sqrt3/2,1]$ of
\[
 P_h(c):=c^4-c^2+hc-h^2=0,
\]
with $C_L(0)=1$.  In $\mathcal A_T$ the selector $c\le2p$ keeps the smaller
geometric root
\[
 C_T(p,h)=\frac{2p}{1+\sqrt{4s^2-3}}.
\]
The two expressions agree when $q=0$.

First assume $q\le0$.  If $h\ge3/8$, then $p\ge1/2$ and $s\ge7/8$.  On this
region
\[
 \frac{\partial q}{\partial p}=4s^3-2s+h
 \ge4\left(\frac78\right)^3-2\left(\frac78\right)+\frac38
 =\frac{167}{128}>0.
\]
Moreover
\[
 \frac{d}{dh}q\left(\frac12,h\right)
 =h(4h^2+6h+1)>0.
\]
Thus
\[
 q(p,h)\ge q\left(\frac12,\frac38\right)=\frac{33}{4096}>0,
\]
a contradiction.  Hence $0\le h<3/8$.  At
$c_0=1-h/3$,
\[
 P_h(c_0)=\frac h{81}\left(h^3-12h^2-63h+27\right).
\]
The cubic in parentheses decreases on $[0,3/8]$ and has value $891/512$ at
$3/8$, so this expression is positive for $h>0$.  Also
$c_0>7/8>\sqrt3/2$, and
\[
 P_h'(c)=c(4c^2-2)+h>0\qquad(c\ge\sqrt3/2).
\]
Therefore the selected root lies below $c_0$.  The case $h=0$ gives equality.

Now assume $q>0$.  Put
\[
 r=\sqrt{4s^2-3},\qquad \delta=\frac{p-h}{s}.
\]
The exact identity
\[
 \frac q{s^2}=\frac{r^2-\delta^2}{4}
\]
gives $0\le\delta<r$.  Thus $r>0$ and we may write
$\delta=wr$ with $0\le w<1$.  Then
\[
 p=\frac{s(1+wr)}2,\qquad
 h=\frac{s(1-wr)}2,
\]
and
\[
 C_T(p,h)=\frac{s(1+wr)}{1+r}.
\]
For fixed $s,r$, set
\[
 \Psi(w)=C_T(p,h)+\frac h3.
\]
A direct differentiation gives
\[
 \Psi'(w)=\frac{sr(5-r)}{6(1+r)}>0,
\]
so
\[
 \Psi(w)<\Psi(1)=\frac{s(7-r)}6.
\]
The hypothesis $p\ge1/2$ gives $s(1+wr)=2p\ge1$, and hence
$s(1+r)\ge1$.  This forces $r>1/8$: otherwise
\[
 4s^2(1+r)^2=(r^2+3)(1+r)^2
 \le\frac{193}{64}\frac{81}{64}
 =\frac{15633}{4096}<4.
\]
Finally,
\[
 144-(r^2+3)(7-r)^2
 =(1-r)(r^3-13r^2+39r-3).
\]
On $[1/8,1]$ the cubic factor is increasing because its derivative
$3r^2-26r+39$ is at least $16$, and its value at $1/8$ is $857/512>0$.
Since $1/8<r<1$, it follows that
\[
 \frac{s(7-r)}6<1.
\]
Consequently $C_T(p,h)+h/3<1$, which proves the strict $\mathcal A_T$ case.
\end{proof}

\begin{remark}[Exact domain limitation]
The hypothesis $p\ge1/2$ cannot be removed.  At
\[
 p=h=\frac25
\]
one has $d=12/25<1$, $s=4/5<1$, and $q=-44/625<0$, so the selected
component is $\mathcal A_L$.  At the proposed cap $c_0=13/15$,
\[
 P_{2/5}\left(\frac{13}{15}\right)
 =-\frac{14}{50625}<0,
 \qquad
 P_{2/5}(1)=\frac6{25}>0.
\]
Since $13/15>\sqrt3/2$ and $P_{2/5}$ is strictly increasing on the selected
root interval,
\[
 c_{\max}\left(\frac25,\frac25\right)>\frac{13}{15}.
\]
Thus Lemma~\ref{lem:half-edge-radial-envelope} is a necessary relaxation only
on its stated half-edge domain; it does not define a global replacement for
the fibers $B_c$, $F_c$, or $G_c$.
\end{remark}

\begin{lemma}[CE2 adjacent outer-ratio bound]
\label{lem:ce2-adjacent-outer-ratio}
Let $0<x,y,u,v<1$, and put
\[
 S=x+y,\qquad D=\sqrt{x^2+xy+y^2}.
\]
Assume the exact CE2 relations
\[
 u+v=\frac{D+xy}{S},\qquad uS\ge x,\qquad vS\ge y,
 \qquad x^2+xv+v^2\le1.
\]
Let $a_0,b_0\ge0$ satisfy
\[
 a_0+b_0>1,\qquad a_0^2+a_0b_0+b_0^2\le1,
\]
and define the two boundary tails by
\[
 A=
 \begin{cases}
  1-b_0,&b_0<y,\\
  \max\{0,1-\max\{b_0,v\}\},&b_0\ge y,
 \end{cases}
\]
and
\[
 H=
 \begin{cases}
  1-a_0,&a_0<x,\\
  \max\{0,1-\max\{a_0,u\}\},&a_0\ge x.
 \end{cases}
\]
If $H>0$ and $A+H<1/2$, then the center reach
\[
 d_2^C=\frac{D+xy-uS-y}{S}=v-\frac yS
\]
satisfies
\[
 d_2^C<\frac H3.
\]
\end{lemma}

\begin{proof}
Because $H>0$, its definition leaves exactly two endpoint sources.

\smallskip
\noindent\emph{First source: $H=1-u$.}
Here $a_0\ge x$ and $a_0\le u$.  Define
\[
 K=x+2y-xy-D.
\]
Since $D+xy-y=S-K$, one has
\[
 d_2^C=1-u-\frac KS=H-\frac KS,
 \qquad
 \frac{d_2^C}{H}=1-\frac{K}{SH}.
\]
Put
\[
 b_\circ(x)=\frac{-x+\sqrt{4-3x^2}}2,\qquad
 h(x)=b_\circ(x)-\frac12.
\]
We first claim
\begin{equation}
 H\le\min\left\{\frac yS,h(x)\right\}.
 \label{eq:outer-first-H-bound}
\end{equation}
The inequality $H\le y/S$ follows from $H=1-u$ and $uS\ge x$.
For the other inequality, $A+H<1/2$ says that whichever of $b_0$ and
$v$ produces the $e_{0,1}$ tail is greater than $1/2+H$.  If it is $b_0$,
then $a_0\ge x$ and the disk inequality give
$b_0\le b_\circ(x)$.  If it is $v$, the center-role diameter inequality
$x^2+xv+v^2\le1$ gives $v\le b_\circ(x)$.  In either case
$H<h(x)$, proving \eqref{eq:outer-first-H-bound}.

Set
\[
 m=\min\left\{\frac yS,h(x)\right\}.
\]
We prove $K/(Sm)>2/3$.  First suppose $y/S\le h(x)$ and put $r=y/x$.
Then
\[
 r\le\frac{h(x)}{1-h(x)},\qquad r\le1.
\]
The exact inequality
\[
 \sqrt{1+r+r^2}\le1+\frac r2+\frac{r^2}{2}
\]
follows because the difference of the squares is $r^2(r+1)^2/4$.
Consequently
\[
 \frac Ky\ge\frac32-x-\frac r2
 \ge\frac32-x-\frac{h(x)}{2(1-h(x))}.
\]
Write $b=h(x)+1/2=b_\circ(x)$.  The diameter relation is symmetric, so
$x=b_\circ(b)$.  Define
\[
 F(b)=\frac{-b+\sqrt{4-3b^2}}2+\frac{b-1/2}{3-2b}.
\]
On $1/2\le b\le1$,
\[
 F'(b)=\frac{2}{(3-2b)^2}-\frac12
 -\frac{3b}{2\sqrt{4-3b^2}}<0.
\]
For the last sign, put $z=1-b\in[0,1/2]$.  After moving the rational
term and squaring the nonnegative sides, for $z>0$ it is equivalent to
\[
 \begin{aligned}
 &9(1-z)^2(1+2z)^4\\
 &\qquad-
 (3-4z-4z^2)^2(1+6z-3z^2)>0.
 \end{aligned}
\]
The left side is $zP(z)$, where the Bernstein coefficients of the
degree-$5$ polynomial $P$ on $[0,1/2]$ are
\[
 24,\qquad50,\qquad\frac{364}{5},\qquad\frac{434}{5},\qquad
 \frac{432}{5},\qquad72.
\]
Thus $F$ is decreasing, and
\[
 F(b)\le F\left(\frac12\right)=\frac{\sqrt{13}-1}{4}.
\]
It follows that
\[
 \frac Ky\ge\frac{7-\sqrt{13}}4>\frac23.
\]
Here $Sm=y$, so $K/(Sm)>2/3$.

Now suppose $h(x)\le y/S$, so $m=h(x)$.  For fixed $x$, define
\[
 g(y)=\frac{x+2y-xy-\sqrt{x^2+xy+y^2}}{x+y}.
\]
Then
\[
 g'(y)=\frac{x\{2(1-x)D+x-y\}}{2S^2D}>0.
\]
The sign is immediate for $y\le x$.  For $y>x$, the bound $D\ge y$ gives
\[
 2(1-x)D+x-y\ge x+(1-2x)y
 =x(1-y)+y(1-x)>0.
\]
Let $y_0$ satisfy $y_0/(x+y_0)=h(x)$.  Since $y\ge y_0$,
\[
 \frac{K(x,y)}{Sh(x)}
 \ge\frac{K(x,y_0)}{(x+y_0)h(x)}
 =\frac{K(x,y_0)}{y_0}>\frac23,
\]
where the last inequality is the boundary value from the preceding
subcase.  Hence $K/(Sm)>2/3$ in all cases.  Since $H\le m$,
\[
 \frac{K}{SH}\ge\frac{K}{Sm}>\frac23,
\]
and therefore $d_2^C/H<1/3$.

\smallskip
\noindent\emph{Second source: $H=1-a_0$.}
Now $a_0=1-H$.  The $e_{0,1}$ tail cannot be $A=1-b_0$, since otherwise
\[
 A+H=2-a_0-b_0<\frac12
\]
would imply $a_0+b_0>3/2$, contrary to
$a_0+b_0\le2/\sqrt3$, which follows from the disk inequality.  Thus
$A=1-v$ and
\[
 v>\frac12+H.
\]
For $v$ to determine the tail, $T_0$ reaches the start $y$ of the CE2
interval, so $b_0\ge y$.  The disk inequality becomes
\[
 (1-H)^2+(1-H)y+y^2\le1,
\]
or
\[
 H^2-(2+y)H+y+y^2\le0.
\]
Put
\[
 L(y)=\frac{2+y-\sqrt{4-3y^2}}2.
\]
Since $H<1/2$, this gives $H\ge L(y)$.  Moreover $uS\ge x$ and the
CE2 coupling give
\[
 v\le\frac{D+xy-x}{S},
\]
and hence
\begin{equation}
 \frac{D+xy-x}{S}>\frac12+L(y).
 \label{eq:outer-analytic-premise}
\end{equation}

We now prove the exact analytic implication needed here.  Fix $0<y<1$,
write $L=L(y)$, and suppose \eqref{eq:outer-analytic-premise} holds.
First,
\[
 \frac{D+xy-x}{S}<1.
\]
Indeed, both sides in $D<2x+y-xy$ are positive, and
\[
 (2x+y-xy)^2-D^2
 =x\{y(3-2y)+x(1-y)(3-y)\}>0.
\]
Thus the premise forces $0<L<1/2$.  Set
\[
 r=\frac xy,\qquad R=\sqrt{r^2+r+1},\qquad
 r_0=\frac{3-4L}{3+4L}.
\]
Then
\[
 \frac{D+xy-x}{S}=\frac{R-r(1-y)}{r+1},\qquad
 \frac{D+xy-x-y}{S}=\frac{R-r(1-y)-1}{r+1}.
\]

Suppose first that $0<r\le r_0$.  Using
$R\le1+r/2+r^2/2$ gives
\[
 \frac{R-r(1-y)-1}{r+1}
 \le\frac{r(y-1/2+r/2)}{r+1}.
\]
The right side is convex in $r$, since its second derivative is
$2(1-y)/(1+r)^3>0$, so its maximum on $[0,r_0]$ is at an endpoint.
At $r=0$ it is zero, while
\[
 \frac L3-\frac{r_0(y-1/2+r_0/2)}{r_0+1}
 =\frac{N(L)}{6(3+4L)},
\]
where
\[
 N(L)=16L^2y-8L^2+18L-9y,\qquad
 y=\frac{L-1+\sqrt{1+6L-3L^2}}2.
\]
Write $s=\sqrt{1+6L-3L^2}$.  Then $N(0)=0$ and
\[
 2sN'(L)=s(48L^2-64L+27)-144L^3+240L^2+59L-27.
\]
For $0<L<1/2$, one has $48L^2-64L+27>0$ and
\[
 s\ge1+3L-6L^2,
\]
because the right side is positive and the difference of the squares is
$36L^3(1-L)$.  Therefore
\[
 2sN'(L)\ge2L(-144L^3+192L^2-33L+38)>0.
\]
The Bernstein coefficients of the last cubic on $[0,1/2]$ are
\[
 38,\qquad\frac{65}{2},\qquad43,\qquad\frac{103}{2},
\]
so its positivity is exact.  Thus $N(L)>0$, proving
\begin{equation}
 \frac{D+xy-x-y}{S}<\frac L3
 \label{eq:outer-analytic-conclusion}
\end{equation}
when $r\le r_0$.

It remains to exclude the premise when $r\ge r_0$.  Put
\[
 J(r)=\frac{R-r(1-y)}{r+1}.
\]
Its derivative has the sign of
\[
 \frac{r-1}{2R}-(1-y).
\]
The function $(r-1)/(2R)$ is strictly increasing, since
\[
 \frac{d}{dr}\left(\frac{r-1}{2R}\right)
 =\frac{3(r+1)}{4R^3}>0.
\]
Hence $J$ decreases and then increases, with at most one turning point, so
its maximum on $[r_0,\infty)$ occurs at $r_0$ or in the limit.  The limit is
$y$, and
\[
 y<\frac12+L
\]
because $(3-y)^2-(4-3y^2)=4y^2-6y+5>0$.  At $r=r_0$, again using
$R\le1+r/2+r^2/2$,
\[
 \frac12+L-J(r_0)\ge\frac{N(L)}{(3+4L)^2}>0.
\]
Thus $J(r)<1/2+L$ for every $r\ge r_0$, contradicting the premise.
This completes the proof of \eqref{eq:outer-analytic-conclusion}.

Finally,
\[
 d_2^C=v-\frac yS
 \le\frac{D+xy-x-y}{S}
 <\frac{L(y)}3\le\frac H3.
\]
The two endpoint sources are exhaustive, so the lemma follows.
\end{proof}
