\section{Exhaustive assembly}
\label{sec:assembly}

We now assemble the four mechanisms.  The table is included to make the
exhaustiveness audit visible: its rows are mutually exclusive after the
center type and the value of $N_+$ have been fixed, except for the one row
explicitly marked as a joint application of Strategies~1 and~2.

\begin{center}
\small
\renewcommand{\arraystretch}{1.13}
\begin{tabular}{p{.25\textwidth}p{.52\textwidth}c}
center and row count&exhaustive refinement&route\\ \hline
$\CEzero$, $N_+=0$&all vertex types&1\\
$\CEzero$, $N_+=1$&all six roles $\Vdzero$&4\\
$\CEzero$, $N_+=1$&a $\Vdone$ or $\Vdtwo$ role&1\\
$\CEzero$, $N_+=1$&no $\Vdone/\Vdtwo$ role and a $\Tlike$ role&3\\
$\CEzero$, $N_+\ge2$&all vertex types&3\\ \hline
$\CEone/\CEtwo$, $N_+=0$&all six roles $\Vdzero$&2\\
$\CEone/\CEtwo$, $N_+=0$&a $\Vdone$ or $\Vdtwo$ role&1\\
$\CEone/\CEtwo$, $N_+=0$&no $\Vdone/\Vdtwo$ role and a $\Tlike$ role&2\\ \hline
$\CEone/\CEtwo$, $N_+=1$&all $\Vdzero$, zero gaps&4\\
$\CEone/\CEtwo$, $N_+=1$&all $\Vdzero$, exactly one gap&2\\
$\CEtwo$, $N_+=1$&all $\Vdzero$, exactly two gaps&2\\
$\CEone$, $N_+=1$&a $\Vdone$ or $\Vdtwo$ role&1\\
$\CEtwo$, $N_+=1$&at least two $\Vdone/\Vdtwo$ roles&1\\
$\CEtwo$, $N_+=1$&exactly one $\Vdone/\Vdtwo$ role&1+2\\
$\CEone/\CEtwo$, $N_+=1$&no $\Vdone/\Vdtwo$ role and exactly one $\Tlike$ role&2\\
$\CEone/\CEtwo$, $N_+=1$&no $\Vdone/\Vdtwo$ role and at least two $\Tlike$ roles&1\\
$\CEone/\CEtwo$, $N_+\ge2$&all vertex types&1
\end{tabular}
\end{center}

\begin{lemma}[Exhaustiveness of the gap split]
\label{lem:gap-exhaustion}
On each edge the complement of the two incident vertex-role traces is either
empty or one closed interval; a singleton interval counts as a gap.  Every
edge having a gap has positive-length intersection with the open center
role.  Consequently a $\CEzero$ center permits no gaps, a $\CEone$ center
permits at most one, and a $\CEtwo$ center permits at most two.
\end{lemma}

\begin{proof}
In the coordinate $X_i(x)$ of Section~\ref{sec:structural-reductions}, the
two incident open traces are intervals issuing from $0$ and $1$.  Their
complement is therefore either empty or the single interval
$[B_i,1-A_{i+1}]$, including the equality case.

If this complement is nonempty, each of its points must be covered by
$U_C$: a nonincident vertex role cannot contain an interior point of the
edge, because that point is more than unit distance from the role's
distinguished vertex.  Choose any point of the gap.  Since $U_C$ is open,
its intersection with the edge contains a relative neighborhood of that
point, and hence has positive length.  Thus different gap edges give
different edges counted by $N_E(T_C)$.  Proposition~\ref{prop:ce-classification}
now gives the assertion, including singleton gaps.
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:main}]
Suppose that seven open unit equilateral triangles cover $H$.  By
Lemma~\ref{lem:distinct-roles}, label them as one center role and six vertex
roles.  Proposition~\ref{prop:ce-classification} places the center in exactly
one of $\CEzero,\CEone,\CEtwo$, and~\eqref{eq:N-plus-definition} places the
actual vertex rows in exactly one of $N_+=0$, $N_+=1$, and $N_+\ge2$.

First suppose the center is $\CEzero$.  If $N_+=0$, the perimeter obstruction
in Proposition~\ref{prop:length-branches} applies.  If $N_+\ge2$, the strict
area certificate in Proposition~\ref{prop:area-branches} applies.  Let
$N_+=1$.  Proposition~\ref{prop:vertex-classification} gives exactly three
refinements: all roles are $\Vdzero$; at least one is $\Vdone$ or $\Vdtwo$;
or no such role occurs and at least one role is $\Tlike$.  The first
refinement has zero gaps by Lemma~\ref{lem:gap-exhaustion} and contradicts
Theorem~\ref{thm:zero-gap-obstruction}; the second is closed by
Proposition~\ref{prop:length-branches}; and the third is closed by
Proposition~\ref{prop:area-branches}.

Now suppose the center is $\CEone$ or $\CEtwo$.  When $N_+=0$, the same
vertex-type trichotomy is exhaustive.  The all-$\Vdzero$ and the
no-$\Vdone/\Vdtwo$ but $\Tlike$ refinements contradict
Proposition~\ref{prop:demand-branches}, while the refinement containing a
$\Vdone$ or $\Vdtwo$ role contradicts
Proposition~\ref{prop:length-branches}.  When $N_+\ge2$, the conditional
skeleton obstruction in Proposition~\ref{prop:length-branches} applies.

It remains that the center is $\CEone$ or $\CEtwo$ and $N_+=1$.  If all six
vertex roles are $\Vdzero$, Lemma~\ref{lem:gap-exhaustion} gives zero or one
gap in class $\CEone$ and zero, one, or two gaps in class $\CEtwo$.  The
zero-gap state contradicts Theorem~\ref{thm:zero-gap-obstruction}; the
one-gap states and the $\CEtwo$ two-gap state contradict
Proposition~\ref{prop:demand-branches}.

Suppose instead that a $\Vdone$ or $\Vdtwo$ role occurs.  In class $\CEone$,
or in class $\CEtwo$ when at least two such roles occur,
Proposition~\ref{prop:length-branches} applies.  The remaining possibility is
$\CEtwo$ with exactly one $\Vdone/\Vdtwo$ role.  The exceptional placement
theorem incorporated in Proposition~\ref{prop:demand-branches}, together
with the neighboring-midpoint and conditional-skeleton subcases in
Proposition~\ref{prop:length-branches}, exhausts that hybrid package.

Finally suppose there is no $\Vdone$ or $\Vdtwo$ role but not all roles are
$\Vdzero$.  Then Proposition~\ref{prop:vertex-classification} says that the
remaining non-$\Vdzero$ roles are precisely $\Tlike$.  Exactly one such role
is excluded by Proposition~\ref{prop:demand-branches}, and at least two are
excluded by Proposition~\ref{prop:length-branches}.  Every row of the table
has now produced a contradiction.  Therefore the assumed open cover does not
exist.
\end{proof}

Corollary~\ref{cor:expanded-closed} follows at once from
Proposition~\ref{prop:open-closed-scaled}.
