\subsection{The exact global certificate for the mixed overlaps}
\label{subsec:exact-mixed-overlap}

This subsection proves the two mixed-overlap signs used in
Theorem~\ref{thm:witness-enclosure}.  It first
replaces the exact radial value by rational upper envelopes, then reduces the
mixed residuals to eight integer-polynomial signs.  Three fixed analytic charts
and twenty global Bernstein expansions prove those signs.  No interval
arithmetic, box subdivision, pruning, or branch-and-bound is used.

Retain the notation of Section~\ref{sec:ab-core}.  Thus
\[
 p=1-b,\qquad q=1-a,\qquad
 s=p+q,\qquad m=\min\{p,q\},\qquad M=\max\{p,q\},
\]
\[
 \chi=s^4-s^2+mM,\qquad h=\frac{\sqrt3}{2},
 \qquad c_*=c_{\max}(p,q).
\]
The strict domain gives
\begin{equation}
 mM>(1-s)(2-s),\qquad m>1-s,\qquad s>\frac23.
 \label{eq:global-mixed-domain}
\end{equation}
Put
\[
 F_m(x)=x^4-x^2+mx-m^2,
 \qquad \kappa=F_m'(s)=4s^3-2s+m.
\]
Since $m>1-s$,
\begin{equation}
 \kappa>4s^3-3s+1=(s+1)(2s-1)^2>0.
 \label{eq:global-kappa-positive}
\end{equation}

\subsubsection{Rational radial upper envelopes}

Define
\begin{equation}
 \bar c_L=s-\frac{\chi}{\kappa}\quad(\chi\le0),
 \qquad
 \bar c_T=s-\frac{\chi}{1-m}\quad(\chi\ge0).
 \label{eq:global-branchwise-cbar}
\end{equation}

\begin{lemma}[Branchwise radial upper bounds]
\label{lem:global-branchwise-cbar}
On the corresponding radial cells,
\[
 c_*\le\bar c_L<1,\qquad c_*\le\bar c_T<1.
\]
At $\chi=0$ both upper bounds equal $s=c_*$.
\end{lemma}

\begin{proof}
On the $C_L(m)$ cell, $F_m(s)=\chi\le0$ and $F_m(c_*)=0$.  For
$x\ge s>2/3$ one has $F_m''(x)=12x^2-2>0$, so convexity and
\eqref{eq:global-kappa-positive} give
\[
 0=F_m(c_*)\ge F_m(s)+F_m'(s)(c_*-s),
\]
whence $c_*\le s-\chi/\kappa=\bar c_L$.  Let $U=1-s$.  From
\eqref{eq:global-mixed-domain}, $mM>U(1+U)$, and therefore
\[
 \begin{aligned}
 \chi+U\kappa
 &>U\{m+3s^3-s^2-3s+2\}\\
 &=U\{m+1-4U+8U^2-3U^3\}>0.
 \end{aligned}
\]
Indeed $0<U<1/3$ and
$1-4U+8U^2-3U^3>1-4U+7U^2>0$.  Thus $\bar c_L<1$.

On the other cell put
\[
 E=\sqrt{4s^2-3},\qquad
 m_0=\frac{s(1-E)}2,\qquad M_0=\frac{s(1+E)}2.
\]
Then
\[
 \chi=(m-m_0)(M_0-m),\qquad
 s-c_*=\frac{2(m-m_0)}{1+E}.
\]
Hence
\[
 \frac{\chi}{s-c_*}
 =\frac{1+E}{2}(M_0-m)\le1-m,
\]
because $0\le E\le1$ and $M_0\le1$.  This proves
$c_*\le\bar c_T$, while $\chi>0$ gives $\bar c_T<s<1$.
\end{proof}

Reflect so that $z=a-b\ge0$ and put $U=a+b-1$.  Then
\[
 s=1-U,\qquad m=\frac{1-U-z}{2},\qquad
 D^2=z^2+6U+3U^2=:K(U,z),
\]
\[
 \Xi(U,z):=4\chi
 =1-10U+21U^2-16U^3+4U^4-z^2,
\]
\[
 G(U,z):=2\kappa=5-21U+24U^2-8U^3-z.
\]
Consequently
\begin{equation}
 \bar c_L=1-U-\frac{\Xi(U,z)}{2G(U,z)},
 \qquad
 \bar c_T=1-U-\frac{\Xi(U,z)}{2(1+U+z)}.
 \label{eq:global-rational-cbar}
\end{equation}
Neither expression contains the quartic root or the radial radical
$\sqrt{4s^2-3}$.

\subsubsection{The Gram residuals and exact core reduction}

On the active cell write $\bar c$ for the corresponding expression in
\eqref{eq:global-rational-cbar}, and put
\[
 \bar\eta=h(1-\bar c),\qquad e=1-\bar c,
 \qquad t=2\bar c-1.
\]
Lemma~\ref{lem:global-branchwise-cbar} gives
$0<\bar\eta\le\eta=h(1-c_*)$ when $c_*>2/3$.  Thus the three disks obtained
from $\mathbb D(C,2\eta)$, $\mathbb D(W,\eta)$, and
$\mathbb D(RA,2\eta)$ by replacing $\eta$ with $\bar\eta$ are contained in
the disks already present in the Minkowski sum.

Represent a global vector as $(x,hy)$ and put $C'=R^{-1}C$,
\[
 N_A=\lVert A\rVert^2,\qquad N_C=\lVert C\rVert^2,
 \qquad \nu=\langle A,C'\rangle,
 \qquad \Delta_0=x_Ay_{C'}-y_Ax_{C'}.
\]
The Gram identity is
\[
 h^2\Delta_0^2=N_AN_C-\nu^2.
\]
The two mixed square residuals for the smaller disks factor as
\begin{equation}
 \bar P_A=h^2N_AQ_A,
 \qquad Q_A=\Delta_0^2-\lVert tA-eC'\rVert^2,
 \label{eq:global-QA-factor}
\end{equation}
\begin{equation}
 \bar P_C=h^2N_CQ_C,
 \qquad Q_C=\Delta_0^2-\lVert tC'-eA\rVert^2.
 \label{eq:global-QC-factor}
\end{equation}
All witness coordinates are rational in $U,z,D$.  Substituting
\eqref{eq:global-rational-cbar} into
\eqref{eq:global-QA-factor}--\eqref{eq:global-QC-factor} and reducing modulo
$D^2-K(U,z)$ gives, for $B\in\{L,T\}$ and $X\in\{A,C\}$,
\begin{equation}
 \operatorname{num}(Q_{B,X})
 =32(K+3)^2\{A_{B,X}(U,z)+D B_{B,X}(U,z)\},
 \label{eq:global-core-reduction}
\end{equation}
where $A_{B,X},B_{B,X}\in\mathbb Z[U,z]$.  Every omitted denominator is
strictly positive: it is a positive constant times $(D+3)^4$, the square of
the relevant upper-envelope denominator, and squares of the two nonzero
Newton-derivative numerators.  The term counts are
\[
\begin{array}{c|cc}
(B,X)&\#A_{B,X}&\#B_{B,X}\\ \hline
(L,A)&347&298\\
(L,C)&347&298\\
(T,A)&342&294\\
(T,C)&341&294.
\end{array}
\]
Since $D\ge0$, it remains to prove all eight integer polynomials nonnegative.

\subsubsection{Three fixed charts and global positive bases}

Set
\[
 \mathcal G(U)=1-6U-3U^2,
 \qquad
 H(U)=1-10U+21U^2-16U^3+4U^4,
\]
\[
 U_H=1-\frac{\sqrt3}{2},
 \qquad U_{\max}=\frac2{\sqrt3}-1.
\]
The identities
\[
 4\chi=H(U)-z^2,
 \qquad
 H(U)=(U-1)^2(4U^2-8U+1)
\]
and
\[
 \mathcal G(U)-H(U)
 =4U(1-6U+4U^2-U^3)\ge0\quad(0\le U\le U_H)
\]
show that the radial cells are exactly covered by
\begin{equation}
\begin{array}{ll}
T:&0\le U\le U_H,\quad 0\le z^2\le H(U),\\[1mm]
L_0:&0\le U\le U_H,\quad H(U)\le z^2\le\mathcal G(U),\\[1mm]
L_1:&U_H\le U\le U_{\max},\quad 0\le z^2\le\mathcal G(U).
\end{array}
\label{eq:global-three-cells}
\end{equation}

We use the elementary positive-basis fact that a polynomial whose
coefficients in the tensor Bernstein basis on $[0,1]^2$ are all nonnegative
is nonnegative on that square.  This is one global polynomial identity, not a
subdivision procedure.  All coefficients below lie in $\mathbb Q(\sqrt3)$,
and their signs are decided exactly by rational comparisons.

For the $T$ cell use
\begin{equation}
 U=\frac{(x-1)(3-x)}{4x},
 \qquad z=y\frac{9-x^4}{8x^2},
 \qquad 1\le x\le\sqrt3,
 \quad 0\le y\le1.
 \label{eq:global-T-chart}
\end{equation}
Here
\[
 H\!\left(\frac{(x-1)(3-x)}{4x}\right)
 =\left(\frac{9-x^4}{8x^2}\right)^2,
\]
so the chart covers the whole $T$ cell.  Clearing the positive powers of
$2$ and $x$, then putting $x=1+(\sqrt3-1)r$, gives four global Bernstein
expansions on $[0,1]^2$:
\[
\begin{array}{c|ccc}
&\text{bidegree}&\text{coefficients}&\text{zero coefficients}\\ \hline
A_{T,A}&(88,22)&2047&2\\
B_{T,A}&(80,20)&1701&0\\
A_{T,C}&(88,22)&2047&2\\
B_{T,C}&(80,20)&1701&0.
\end{array}
\]
Every nonzero coefficient is strictly positive.

For an $L$-cell polynomial $F(U,z)$, write
\[
 F(U,z)=E_F(U,w)+zO_F(U,w),\qquad w=z^2,
\]
and put
\[
 R_F(U,w)=E_F(U,w)^2-wO_F(U,w)^2.
\]
The implications $E_F\ge0$ and $R_F\ge0$ give
$E_F\ge\sqrt w\,|O_F|$, hence $F\ge0$.  Use the two fixed charts
\begin{equation}
 U=U_Hr,
 \qquad
 w=H(U)+s\{\mathcal G(U)-H(U)\}
 \label{eq:global-L0-chart}
\end{equation}
for $L_0$, and
\begin{equation}
 U=U_H+(U_{\max}-U_H)r,
 \qquad w=s\mathcal G(U)
 \label{eq:global-L1-chart}
\end{equation}
for $L_1$, with $0\le r,s\le1$.  The global Bernstein expansions of
$E_F$ and $R_F$ have the following bidegrees and coefficient counts:
\[
\begin{array}{c|cc|cc}
F&L_0:E_F&L_0:R_F&L_1:E_F&L_1:R_F\\ \hline
A_{L,A}&(46,11);564&(92,22);2139&(26,11);324&(52,22);1219\\
B_{L,A}&(42,10);473&(84,20);1785&(24,10);275&(48,20);1029\\
A_{L,C}&(46,11);564&(92,22);2139&(26,11);324&(52,22);1219\\
B_{L,C}&(42,10);473&(84,20);1785&(24,10);275&(48,20);1029.
\end{array}
\]
Every coefficient in these sixteen expansions is strictly positive.
Therefore all eight polynomials in \eqref{eq:global-core-reduction} are
nonnegative on the corresponding radial cells.

\begin{lemma}[Exact mixed-cap overlaps]
\label{lem:exact-mixed-cap-overlaps}
In the regime $c_*>2/3$, the tangent witnesses defined above satisfy
\[
 I(C,2\eta)\cap I(W,\eta)\ne\varnothing,
 \qquad
 I(W,\eta)\cap I(RA,2\eta)\ne\varnothing.
\]
\end{lemma}

\begin{proof}
Since $D\ge0$, the eight signs prove $Q_A,Q_C\ge0$ for $z\ge0$ by
\eqref{eq:global-core-reduction}; reflection supplies $z\le0$.
Equations~\eqref{eq:global-QA-factor}--\eqref{eq:global-QC-factor} give the two
mixed cap overlaps for the smaller disks, hence for the original disks.
\end{proof}
